---
title: "ART_effects"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Libraries}
library(tidyverse)
library(tidyr)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
library(readxl)
devtools::install_github("BershteynLab/EMODAnalyzeR")
```


```{r}
# Confidence interval functions
lower_ci <- function(mean, se, n, conf_level = 0.95){
  lower_ci <- mean - qt(1 - ((1 - conf_level) / 2), n - 1) * se
  return(lower_ci)
}
upper_ci <- function(mean, se, n, conf_level = 0.95){
  upper_ci <- mean + qt(1 - ((1 - conf_level) / 2), n - 1) * se
  return(upper_ci)
}
```



# HIV-Depression model postprocessing

The "minimal scenario" set of HIV-CMD interactions
1. Depression dynamics
  1. Age/sex-specific annual incidence of depression
  2. HIV+ status also increases depression incidence
  3. Relapse rate equal to incidence rate
2. Depression-caused increase to incidence - CoitalActRiskFactor increases from 1 to 1.646
3. Depression-caused delays to diagnosis (2/3 of depressed skip diagnosis)
4. Depression-caused dropout from ART (mean time 5 years for depressed, 10 years for non-depressed)
5. Depression-caused non-adherence to ART


First order of business will be to isolate the effects of reducing the efficacy of ART
1. decouple-adh_ART - lower art adherence only + ART 
2. decouple-adh_noART - lower art adherence + no ART
3. decouple-drop_ART - increased ART dropout + ART - the baseline for this is the same as decouple-adh_noART
4. decouple-risk_ART - increased transmission/acquisition risk + ART
5. decouple-risk_noART - increased transmission/acquisition risk + no ART
6. baseline-inc_ART - increased depression incidence among PLHIV + ART
7. baseline-inc_noART - increased depression incidence among PLHIV + no ART 


# Read in the data

## Decoupled baseline

No interactions, with and without ART

### ART

```{r}
sim.results.decouple.art <- EMODAnalyzeR::read.simulation.results.bigpurple(
  #experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-decouple_ART___2023_10_12_18_09_47_563366",
  experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-new_decouple_ART___2023_10_18_18_43_06_263619",
    scenario_name = 'decouple.art',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 15,
  max_age_inclusive = 50
)


# sim.results.decouple.art <- EMODAnalyzeR::read.simulation.results(
#   #results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/croi/Baseline-campaign_MATUMAINI_202305_decouple-decouple_ART/ReportHIVByAgeAndGender/",
#   results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/minimal/Baseline-campaign_MATUMAINI_202305_decouple-new_decouple_ART/ReportHIVByAgeAndGender/",
#   scenario_name = 'decouple.art',
#   summarize_columns = c("Population","Infected", "On_ART",
#                         "Died", "Died_from_HIV",
#                         "Newly.Infected","Diagnosed"),
#   stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
#   min_age_inclusive = 0,
#   max_age_inclusive = 99
# )

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.decouple.art %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.decouple.art <- sim.results.decouple.art %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

### No ART

```{r}
# sim.results.decouple.noart <- EMODAnalyzeR::read.simulation.results(
#   results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/minimal/Baseline-campaign_MATUMAINI_202305_decouple-new_decouple_noART/ReportHIVByAgeAndGender/",
#   # results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/art/Baseline-campaign_MATUMAINI_202305_decouple-decouple_noART/ReportHIVByAgeAndGender/",
#   scenario_name = 'decouple.noart',
#   summarize_columns = c("Population","Infected", "On_ART",
#                         "Died", "Died_from_HIV",
#                         "Newly.Infected","Diagnosed"),
#   stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
#   min_age_inclusive = 0,
#   max_age_inclusive = 99
# )

sim.results.decouple.noart <- EMODAnalyzeR::read.simulation.results.bigpurple(
  #experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-decouple_noART___2023_10_12_18_09_00_359386/",
  experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-new_decouple_noART___2023_10_18_18_42_14_798658/",
    scenario_name = 'decouple.noart',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 15,
  max_age_inclusive = 50
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.decouple.noart %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.decouple.noart <- sim.results.decouple.noart %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

## ART Adherence

### ART
```{r}
# sim.results.adh.art <- EMODAnalyzeR::read.simulation.results(
#   # results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/art/Baseline-campaign_MATUMAINI_202305_decouple-adh_ART/ReportHIVByAgeAndGender",
#   results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/minimal/Baseline-campaign_MATUMAINI_202305_decouple-new_adh_ART/ReportHIVByAgeAndGender/",
#   scenario_name = 'adh_ART',
#   summarize_columns = c("Population","Infected", "On_ART",
#                         "Died", "Died_from_HIV",
#                         "Newly.Infected","Diagnosed"),
#   stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
#   min_age_inclusive = 0,
#   max_age_inclusive = 99
# )

sim.results.adh.art <- EMODAnalyzeR::read.simulation.results.bigpurple(
  #experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-adh_ART___2023_10_12_18_10_56_333947/",
  experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-new_adh_ART___2023_10_17_17_55_12_533863/",
    scenario_name = 'adh.art',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 15,
  max_age_inclusive = 50
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.adh.art %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.adh.art <- sim.results.adh.art %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

### Maximum effect size ART adherence
```{r}
# sim.results.adh.art <- EMODAnalyzeR::read.simulation.results(
#   # results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/art/Baseline-campaign_MATUMAINI_202305_decouple-adh_ART/ReportHIVByAgeAndGender",
#   results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/minimal/Baseline-campaign_MATUMAINI_202305_decouple-new_adh_ART/ReportHIVByAgeAndGender/",
#   scenario_name = 'adh_ART',
#   summarize_columns = c("Population","Infected", "On_ART",
#                         "Died", "Died_from_HIV",
#                         "Newly.Infected","Diagnosed"),
#   stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
#   min_age_inclusive = 0,
#   max_age_inclusive = 99
# )

sim.results.adh.art.max <- EMODAnalyzeR::read.simulation.results.bigpurple(
  #experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-adh_ART___2023_10_12_18_10_56_333947/",
  #experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-new_adh_ART___2023_10_17_17_55_12_533863/",
  experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-new_adh_ART_xtreem___2023_10_19_11_53_58_458404/",
    scenario_name = 'adh.art',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 15,
  max_age_inclusive = 50
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.adh.art.max %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.adh.art.max <- sim.results.adh.art.max %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```


### No ART

```{r}
# sim.results.adh.noart <- EMODAnalyzeR::read.simulation.results(
#   results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/art/Baseline-campaign_MATUMAINI_202305_decouple-adh_noART/ReportHIVByAgeAndGender",
#   scenario_name = 'adh_noART',
#   summarize_columns = c("Population","Infected", "On_ART",
#                         "Died", "Died_from_HIV",
#                         "Newly.Infected","Diagnosed"),
#   stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
#   min_age_inclusive = 0,
#   max_age_inclusive = 99
# )

sim.results.adh.noart <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-adh_noART___2023_10_12_18_10_22_752467/",
    scenario_name = 'adh.noart',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 15,
  max_age_inclusive = 50
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.adh.noart %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.adh.noart <- sim.results.adh.noart %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

## ART dropout

```{r}
sim.results.drop.art <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/art/Baseline-campaign_MATUMAINI_202305_decouple-drop_ART/ReportHIVByAgeAndGender/",
  scenario_name = 'dropout_ART',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.drop.art %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.drop.art <- sim.results.drop.art %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )
```

## Increased risk

### ART
```{r}
sim.results.risk.art <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/art/Baseline-campaign_MATUMAINI_202305_decouple-risk_ART/ReportHIVByAgeAndGender/",
  scenario_name = 'risk_ART',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.risk.art %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.risk.art <- sim.results.risk.art %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )
```

### No ART
```{r}
sim.results.risk.noart <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/art/Baseline-campaign_MATUMAINI_202305_decouple-risk_noART/ReportHIVByAgeAndGender/",
  scenario_name = 'risk_noART',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.risk.noart %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.risk.noart <- sim.results.risk.noart %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )
```


## Increased depression prevalence for PLHIV 

### ART

```{r}
sim.results.inc.art <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/art/Baseline-campaign_MATUMAINI_202305-inc_ART/ReportHIVByAgeAndGender/",
  scenario_name = 'risk_ART',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.inc.art %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.inc.art <- sim.results.inc.art %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

### No ART

```{r}
sim.results.inc.noart <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/art/Baseline-campaign_MATUMAINI_202305-inc_noART/ReportHIVByAgeAndGender/",
  scenario_name = 'risk_ART',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.inc.noart %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.inc.noart <- sim.results.inc.noart %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

## Delays to ART 

```{r}
sim.results.delay <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/art/Baseline-campaign_MATUMAINI_202305-art_delay/ReportHIVByAgeAndGender/",
  scenario_name = 'delay',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.delay %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.delay <- sim.results.delay %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )
```




## Combine datasets

```{r}
#sim.results.all <- rbind(sim.results.base, sim.results.adh, sim.results.delay, sim.results.drop, sim.results.risk)
sim.results.all <- rbind(sim.results.adh.art, #sim.results.adh.noart, 
                         sim.results.decouple.art, sim.results.decouple.noart)
```

# Plot Results 

## HIV Prevalence over time

```{r}
ingest.file.base = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_Baseline_MalariaOngoing_original/Data/calibration_ingest_form_Nyanza.xlsm"

obs.prev.sheet.base <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-Prevalence")
```


```{r, fig.width=8, fig.height=8}
#p <- EMODAnalyzeR::emodplot.prevalence(sim.results %>% filter(Age <= 50, Age >=15), 
#                                       1990, 20240)
p <- EMODAnalyzeR::emodplot.prevalence(sim.results.all %>% filter(Age <= 50, Age >=15), 
                                       1980, 2040)

p +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    ylab("HIV Prevalence (%)") + 
  #scale_color_manual(values=c("blue","red","darkgreen","orange")) +
  geom_point(data = obs.prev.sheet.base %>%
               filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
             mapping = aes(x = Year, y = Prevalence)) + 
  geom_errorbar(data = obs.prev.sheet.base %>%
             filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
             mapping = aes(x = Year, ymin = lb, ymax = ub))

data <- EMODAnalyzeR::calculate.prevalence(
  sim.results.all %>% filter(Age <= 50, Age >=15),
         stratify_columns = c("Year", "Gender", "sim.id", "scenario_name"),
         numerator = "Infected",
         denominator = "Population")

data.mean <- data %>% filter(Year >= 2004) %>% 
  group_by(Year, Gender, scenario_name) %>%
  summarize(sum(Infected))

data.mean <- data %>%
    dplyr::group_by(Year, Gender, scenario_name) %>%
    dplyr::summarise(Prevalence = mean(Prevalence), .groups = 'keep') %>% 
  mutate(ART = case_when(
    scenario_name == "adh_ART" ~ "art",
    scenario_name == "adh.noart" ~ "noart",
    scenario_name == "decouple.art" ~ "art",
    scenario_name == "decouple.noart" ~ "noart"
  ))

ggplot(data.mean) +
    geom_line(data=subset(data.mean, (1980 <= Year) & (Year <= 2040)),
              aes(x=Year, y=Prevalence, group=scenario_name, color=scenario_name), linewidth=.75) +
    facet_wrap(ART~ Gender, ncol=2) +
    xlab("Year")+
    #xlim(c(date.start, date.end)) +
    ylab("Prevalence") +
    theme_bw(base_size=16) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    scale_x_continuous(breaks = seq(1980,2040,10)) +
    theme(legend.position="bottom") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(strip.background = element_rect(colour="black", fill="white")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_color_manual(values=c("black", "blue","red","darkgreen","orange"))

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/minimal_HIV_prev.pdf",
#        width = 8, height = 6, units = "in")
```
## HIV deaths

```{r}
 data <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>%
  filter(Year >= 1985, Year <=2025) %>% 
  group_by(Year, Gender, sim.ix, sim.id, scenario_name) %>% 
  summarize(Deaths = sum(Died_from_HIV * pop.scaling.factor), .groups = 'keep') %>%  
  ungroup()

data.mean <- data %>% 
  group_by(Year, Gender, scenario_name) %>% 
  dplyr::summarise(Deaths = mean(Deaths), .groups = 'keep') %>% 
  mutate(ART = case_when(
    scenario_name == "adh_ART" ~ "art",
    scenario_name == "adh_noART" ~ "noart",
    scenario_name == "decouple.art" ~ "art",
    scenario_name == "decouple.noart" ~ "noart"
  ))

p <- EMODAnalyzeR::emodplot.by_gender(data, 1990, 2025, 
                        "Deaths", title = "HIV deaths") 

p + #scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab("") + 
  #scale_color_manual(values = c("blue","red"))
  scale_color_manual(values = c("blue","red","darkgreen","orange"))


# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/croi_HIV_deaths.pdf",
#       width = 8, height = 6, units = "in")
```

### Calculate deaths averted

```{r}
# at baseline
(data.mean %>% filter(scenario_name == "decouple.noart")  %>% .$Deaths %>% sum) - (data.mean %>% filter(scenario_name == "decouple.art")  %>% .$Deaths %>% sum)

```


```{r}
# When we add adherence
(data.mean %>% filter(scenario_name == "decouple.noart")  %>% .$Deaths %>% sum) - (data.mean %>% filter(scenario_name == "adh_ART")  %>% .$Deaths %>% sum)
```

```{r}
data <- sim.results.all %>%
  #mutate(Year = ceiling(Year)) %>% 
  filter(Year >= 2003, Year <=2025) %>% 
  group_by(sim.ix, scenario_name) %>% 
  summarize(Deaths = sum(Died_from_HIV * pop.scaling.factor), 
  #summarize(Deaths = sum(Died_from_HIV/Infected * pop.scaling.factor), 
            OnART = sum(On_ART/2 * pop.scaling.factor), # factor of 2 to avoid double counting
            PLHIV = sum(Infected/2 * pop.scaling.factor),
            .groups = 'keep')
```

Deaths Averted

```{r}
art.benefit <- data %>% 
  pivot_wider(id_cols = c("sim.ix"), names_from=c("scenario_name"), values_from = c("Deaths", "OnART", "PLHIV")) %>% 
  # This is the number of deaths averted
  # deaths is higher without ART, should be positive
  mutate(baseline.averted = Deaths_decouple.noart - Deaths_adh_ART, 
         decouple.averted = Deaths_decouple.noart - Deaths_decouple.art) %>% 
  # find the difference in ART benefit, and the percent difference 
  # we expect that ART benefit is *smaller* if people are depressed
  mutate(averted.difference = baseline.averted - decouple.averted,
         averted.pct = (baseline.averted - decouple.averted)/decouple.averted) 

art.benefit %>% 
  ungroup() %>% 
  summarize(averted.difference = mean(averted.difference),
            averted.pct = mean(averted.pct))

```

## HIV cases

```{r}
 data <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>%
  filter(Year >= 1985, Year <=2025) %>% 
  group_by(Year, Gender, sim.id, sim.ix, scenario_name) %>% 
  summarize(NewCases = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>%  
  ungroup()

data.mean <- data %>% 
  group_by(Year, Gender, scenario_name) %>% 
  dplyr::summarise(NewCases = mean(NewCases), .groups = 'keep')


p <- EMODAnalyzeR::emodplot.by_gender(data, 1990, 2025, 
                        "NewCases", title = "New HIV Infections") 

p + #scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab("") + 
  scale_color_manual(values = c("blue","red","darkgreen","red"))
```
### Calculate New Cases averted

```{r}
# at baseline
(data.mean %>% filter(scenario_name == "decouple.noart")  %>% .$NewCases %>% sum) - (data.mean %>% filter(scenario_name == "decouple.art")  %>% .$NewCases %>% sum)

```


```{r}
# When we add adherence
(data.mean %>% filter(scenario_name == "decouple.noart")  %>% .$NewCases %>% sum) - (data.mean %>% filter(scenario_name == "adh_ART")  %>% .$NewCases %>% sum)

```


```{r}
data <- sim.results.all %>%
  #mutate(Year = ceiling(Year)) %>% 
  filter(Year >= 2005, Year <=2025) %>% 
  group_by(sim.ix, scenario_name) %>% 
  summarize(NewInf = sum(Newly.Infected * pop.scaling.factor), 
            OnART = sum(On_ART * pop.scaling.factor), # factor of 2 to avoid double counting
            .groups = 'keep')

art.benefit <- data %>% 
  pivot_wider(id_cols = c("sim.ix"), names_from=c("scenario_name"), values_from = c("NewInf", "OnART")) %>% 
  # This is the number of deaths averted
  # deaths is higher without ART, should be positive
  mutate(baseline.averted = NewInf_decouple.noart - NewInf_adh_ART, 
         decouple.averted = NewInf_decouple.noart - NewInf_decouple.art) %>% 
  # find the difference in ART benefit, and the percent difference 
  # we expect that ART benefit is *smaller* if people are depressed
  mutate(averted.difference = baseline.averted - decouple.averted,
         averted.pct = (baseline.averted - decouple.averted)/decouple.averted) 

art.benefit %>% 
  ungroup() %>% 
  summarize(averted.difference = mean(averted.difference),
            averted.pct = mean(averted.pct))
```

```{r}
art.benefit %>% 
  ungroup() %>% 
  summarize(averted.difference = mean(averted.difference),
            averted.pct = mean(averted.pct))
```