---
title: "croi_scenarios.Rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Libraries}
library(tidyverse)
library(tidyr)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
library(readxl)
devtools::install_github("BershteynLab/EMODAnalyzeR")
```


```{r}
# Confidence interval functions
lower_ci <- function(mean, se, n, conf_level = 0.95){
  lower_ci <- mean - qt(1 - ((1 - conf_level) / 2), n - 1) * se
  return(lower_ci)
}
upper_ci <- function(mean, se, n, conf_level = 0.95){
  upper_ci <- mean + qt(1 - ((1 - conf_level) / 2), n - 1) * se
  return(upper_ci)
}
```



# HIV-Depression model postprocessing - CROI abstract

The "minimal scenario" set of HIV-CMD interactions
1. Depression dynamics
  1. Age/sex-specific annual incidence of depression
  2. HIV+ status also increases depression incidence
  3. Relapse rate equal to incidence rate
2. Depression-caused increase to incidence - CoitalActRiskFactor increases from 1 to 1.646
3. Depression-caused delays to diagnosis (2/3 of depressed skip diagnosis)
4. Depression-caused dropout from ART (mean time 5 years for depressed, 10 years for non-depressed)
5. Depression-caused non-adherence to ART

Simulating five scenarios
1. Baseline - with all HIV-CMD, ART
2. Decoupled - without the HIV-CMD interactions, ART
3. Baseline - with all HIV-CMD interactions, no ART
4. Decoupled - without the HIV-CMD interactions, no ART
5. NoAHIV - no HIV

# Read in the data

## Baseline-ART

```{r}
# Baseline-ART scenario run
# res.path.cmd = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305-baseline_ART___2023_09_22_11_37_10_209224"
# 
# sim.results <- EMODAnalyzeR::read.simulation.results.bigpurple(
#   res.path.cmd,
#   scenario_name = 'baseline.art',
#   summarize_columns = c("Population","Infected", "On_ART",
#                         "Died", "Died_from_HIV",
#                         "Newly.Infected","Diagnosed"),
#   stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
#   min_age_inclusive = 0,
#   max_age_inclusive = 99
# )

sim.results <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/croi/Baseline-campaign_MATUMAINI_202305-baseline_ART/ReportHIVByAgeAndGender/",
  scenario_name = 'baseline.art',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results <- sim.results %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

## Decoupled with ART

```{r}
# Decoupled-ART scenario run
# res.path.cmd = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-decouple_ART___2023_09_22_11_41_29_774260"
# 
# sim.results.dec <- EMODAnalyzeR::read.simulation.results.bigpurple(
#   res.path.cmd,
#   scenario_name = 'decouple.art',
#   summarize_columns = c("Population","Infected", "On_ART",
#                         "Died", "Died_from_HIV",
#                         "Newly.Infected","Diagnosed"),
#   stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
#   min_age_inclusive = 0,
#   max_age_inclusive = 99
# )

sim.results.dec <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/croi/Baseline-campaign_MATUMAINI_202305_decouple-decouple_ART/ReportHIVByAgeAndGender/",
  scenario_name = 'decouple.art',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.dec %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.dec <- sim.results.dec %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

## Baseline No ART
```{r}
# Baseline-No ART scenario run
# res.path.cmd = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305-baseline_noART___2023_09_22_11_39_23_843593"
# 
# sim.results.noart <- EMODAnalyzeR::read.simulation.results.bigpurple(
#   res.path.cmd,
#   scenario_name = 'baseline.noart',
#   summarize_columns = c("Population","Infected", "On_ART",
#                         "Died", "Died_from_HIV",
#                         "Newly.Infected","Diagnosed"),
#   stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
#   min_age_inclusive = 0,
#   max_age_inclusive = 99
# )

# Path to scratch directory:
# /gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305-baseline_noART___2023_09_22_11_39_23_843593

sim.results.noart <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/croi/Baseline-campaign_MATUMAINI_202305-baseline_noART/ReportHIVByAgeAndGender/",
  scenario_name = 'baseline.noart',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.noart %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.noart <- sim.results.noart %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

Checking that noART actually has no ART in it
```{r}
sim.results.noart$On_ART %>% summary

```



## Decoupled No ART
```{r}
# Decoupled-No ART scenario run
# res.path.cmd = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple-decouple_noART___2023_09_22_11_43_25_438993"
# 
# sim.results.decnoart <- EMODAnalyzeR::read.simulation.results.bigpurple(
#   res.path.cmd,
#   scenario_name = 'decouple.gnoart',
#   summarize_columns = c("Population","Infected", "On_ART",
#                         "Died", "Died_from_HIV",
#                         "Newly.Infected","Diagnosed"),
#   stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
#   min_age_inclusive = 0,
#   max_age_inclusive = 99
# )

sim.results.decnoart <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/croi/Baseline-campaign_MATUMAINI_202305_decouple-decouple_noART/ReportHIVByAgeAndGender/",
  scenario_name = 'decouple.noart',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.decnoart %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.decnoart <- sim.results.decnoart %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )
```

Checking that noART actually has no ART in it
```{r}
sim.results.decnoart$On_ART %>% summary

```


## Combine datasets
```{r}
sim.results.all <- rbind(sim.results, sim.results.dec, sim.results.noart, sim.results.decnoart)
```


# Plot Results 

## HIV Prevalence over time

```{r}
ingest.file.base = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_Baseline_MalariaOngoing_original/Data/calibration_ingest_form_Nyanza.xlsm"

obs.prev.sheet.base <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-Prevalence")
```


```{r, fig.width=8}
#p <- EMODAnalyzeR::emodplot.prevalence(sim.results %>% filter(Age <= 50, Age >=15), 
#                                       1990, 20240)
p <- EMODAnalyzeR::emodplot.prevalence(sim.results.all %>% filter(Age <= 50, Age >=15), 
                                       1980, 2040)

p +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    ylab("HIV Prevalence (%)") + 
  scale_color_manual(values=c("blue","red","darkgreen","orange")) +
  geom_point(data = obs.prev.sheet.base %>%
               filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
             mapping = aes(x = Year, y = Prevalence)) + 
  geom_errorbar(data = obs.prev.sheet.base %>%
             filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
             mapping = aes(x = Year, ymin = lb, ymax = ub))


# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/minimal_HIV_prev.pdf",
#        width = 8, height = 6, units = "in")
```

## HIV Age-Prevalence Curves

```{r, fig.width=8, fig.height=8}
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65)
subset_years = c(2003, 2007, 2008, 2012, 2018)

p <- EMODAnalyzeR::emodplot.age_prevalence(sim.results %>% filter(scenario_name == "minimal"), 
                                           subset_years = subset_years, 
                                           age_bins = age_bins,
                                           title = "HIV Age-Prevalence Curves")

p + theme(aspect.ratio = .15) + 
  geom_point(data = obs.prev.sheet.base %>% 
    filter(Province == "All", 
           Gender %in% c("Male", "Female"),  
           AgeBin != "[15:50)") %>% 
    mutate(AgeBin_index = factor(AgeBin, labels = 1:10)),
  mapping = aes(x = AgeBin_index, y = Prevalence)) + 
  scale_color_manual(values="blue")

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/minimal_HIV_age_prev.pdf",
       width = 8, height = 6, units = "in")
```

## Numbers on ART over time 

```{r}
ingest.file.base = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_Baseline_MalariaOngoing_original/Data/calibration_ingest_form_Nyanza.xlsm"

obs.onart.sheet <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-OnART")
```


```{r, fig.width=8}
sim.onart <- sim.results.all %>% 
  dplyr::group_by(Year, Gender, sim.id, scenario_name) %>% 
  dplyr::summarize(On_ART = sum(On_ART * pop.scaling.factor), .groups = "keep") %>% 
  ungroup()

p <- EMODAnalyzeR::emodplot.by_gender(sim.onart, 2000, 2025, 
                        "On_ART", title = "Population on ART") + 
    ylab("Number on ART")

p + 
  geom_point(data = obs.onart.sheet %>% 
               filter(Province != "All", 
                      Gender %in% c("Male", "Female"), 
                      AgeBin == "[15:100)") %>%
              group_by(Year, Gender) %>% 
              summarize(OnART = sum(OnART)) %>% ungroup(),
              mapping = aes(x = Year, y = OnART)) + 
  geom_errorbar(data = obs.onart.sheet %>% 
                  filter(Province != "All", 
                         Gender %in% c("Male", "Female"), 
                         AgeBin == "[15:100)") %>%
              group_by(Year, Gender) %>% 
              summarize(OnART = sum(OnART)) %>% ungroup() %>% 
              mutate(lb = OnART - OnART/5,
                     ub = OnART + OnART/5),
              mapping = aes(x = Year, ymin = lb, ymax = ub)) + 
  scale_color_manual(values = c("blue","red","darkgreen","orange"))

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/minimal_onART.pdf",
#        width = 8, height = 6, units = "in")
```
## 90-90-90 

### Diagnosis coverage over time

```{r}
data <- sim.results %>% 
  filter(Age >=15) %>% 
  group_by(Year, Gender,sim.id,scenario_name) %>% 
  summarize(Diagnosed = sum(Diagnosed), Infected = sum(Infected), .groups = "keep") %>% 
  ungroup() %>% 
  mutate(Diagnosed = case_when(Infected == 0 ~ 0,
                               Infected > 0 ~ Diagnosed/Infected)) 

p <- EMODAnalyzeR::emodplot.by_gender(data, 2000, 2040, 
                        "Diagnosed", title = "Diagnosed PLHIV") 

p + scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab("% PLHIV Diagnosed") + 
  scale_color_manual(values = c("blue","red"))

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/minimal_diagnosed.pdf",
       width = 8, height = 6, units = "in")
```

### ART coverage over time

```{r}
data <- sim.results %>% 
  filter(Age >=15) %>% 
  group_by(Year, Gender,sim.id,scenario_name) %>% 
  summarize(On_ART = sum(On_ART), Diagnosed = sum(Diagnosed), .groups = "keep") %>% 
  ungroup() %>% 
  mutate(On_ART = case_when(On_ART == 0 ~ 0,
                               On_ART > 0 ~ On_ART/Diagnosed)) 

p <- EMODAnalyzeR::emodplot.by_gender(data, 2000, 2040, 
                        "On_ART", title = "ART Coverage") 

p + scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab("% Diagnosed and On ART") + 
  scale_color_manual(values = c("blue","red"))

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/minimal_art_coverage.pdf",
       width = 8, height = 6, units = "in")
```

## Incidence

### New HIV Infections

```{r}
 data <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>%
  filter(Year >= 1985, Year <=2025) %>% 
  group_by(Year, Gender, sim.id, sim.ix, scenario_name) %>% 
  summarize(NewCases = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>%  
  ungroup() %>% 
  group_by(Year, Gender, sim.id, sim.ix, scenario_name) %>% 
  summarize(NewCases.sd = sd(NewCases), NewCases = mean(NewCases)) %>% 
  ungroup()# %>% 
  
p <- EMODAnalyzeR::emodplot.by_gender(data, 1990, 2025, 
                        "NewCases", title = "New HIV Infections") 

p + #scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab("") + 
  scale_color_manual(values = c("blue","red","darkgreen","orange"))


# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/croi_HIV_new_cases.pdf",
#        width = 8, height = 6, units = "in")


```
CROI measurement of new infections: Absolute and percent difference of new infections with and without coupling HIV together
```{r}
new.infections.difference <- data %>% 
  pivot_wider(id_cols = c("Year", "Gender", "sim.ix"), names_from=c("scenario_name"), values_from = c("NewCases")) %>% 
  mutate(diff = baseline.art - decouple.art) %>% 
  group_by(sim.ix) %>% 
  summarize(diff = sum(diff), baseline.art = sum(baseline.art), decouple.art = sum(decouple.art)) %>% 
  mutate(pct.diff = diff/decouple.art) 
# %>% 
#   group_by(sim.ix) %>% 
#   summarize(diff = mean(diff), diff.sd = sd(diff),
#             pct.diff = mean(pct.diff), pct.diff.sd = sd(pct.diff),
#             baseline.art = mean(baseline.art), baseline.art.sd = sd(baseline.art),
#             decouple.art = mean(decouple.art), decouple.art.sd = sd(decouple.art))

(mean(new.infections.difference$decouple.art) - mean(new.infections.difference$baseline.art))/mean(new.infections.difference$decouple.art) 


mean(new.infections.difference$diff)

mean(new.infections.difference$diff/new.infections.difference$decouple.art)
sd(new.infections.difference$diff/new.infections.difference$decouple.art)

mean(new.infections.difference$pct.diff)

sd(new.infections.difference$pct.diff)

c(mean(new.infections.difference$diff),
  lower_ci(mean(new.infections.difference$diff), 
         sd(new.infections.difference$diff)/sqrt(250),
         n = 250,
         conf_level = .95),
  upper_ci(mean(new.infections.difference$diff), 
         sd(new.infections.difference$diff)/sqrt(250),
         n = 250,
         conf_level = .95)
)


c(mean(new.infections.difference$pct.diff),
  lower_ci(mean(new.infections.difference$pct.diff), 
         sd(new.infections.difference$pct.diff)/sqrt(250),
         n = 250,
         conf_level = .95),
  upper_ci(mean(new.infections.difference$pct.diff), 
         sd(new.infections.difference$pct.diff)/sqrt(250),
         n = 250,
         conf_level = .95)
)


```

Cumulative cases
```{r}
data %>% group_by(sim.ix, scenario_name) %>% summarise(NewCases = sum(NewCases)) %>% 
  group_by(scenario_name) %>% 
  summarize(NewCases.sd = sd(NewCases), NewCases = mean(NewCases))


c(1242727, lower_ci(1242727,113998.6	/sqrt(250), 250, .95), upper_ci(1242727,113998.6	/sqrt(250), 250, .95))
```



### Incidence by Depression Status

 
```{r, fig.width=8}
data <- sim.results %>% #filter(scenario_name == "minimal")%>%
  mutate(Year_Integer = floor(Year-.5)) %>% 
  mutate(cmd = case_when(IP_Key.CMDStatus == 'CMD_pos' ~ "Depressed",
                         IP_Key.CMDStatus != 'CMD_pos' ~ "Not Depressed")) %>% 
  group_by(Year_Integer, Year, Gender, sim.id, scenario_name, cmd) %>% 
  summarize(Newly.Infected = sum(Newly.Infected), 
            Infected = sum(Infected),
            Population = sum(Population), 
            .groups = 'keep') %>%  
  ungroup()

trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender+sim.id+scenario_name+cmd, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender+sim.id+scenario_name + cmd, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender","sim.id","scenario_name","cmd")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","sim.id","scenario_name", "cmd"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population-(trajectories_IRoverall$Newly.Infected/2))
trajectories_IRoverall <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

data.mean <- trajectories_IRoverall %>% group_by(Year, Gender, scenario_name, cmd) %>% 
  summarize(Incidence = mean(incidence), Incidence.sd = sd(incidence), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

# Plot  
p = ggplot() +
  geom_line(data.mean, mapping = aes(x = Year, y = Incidence, color = cmd), 
    size = 1.0) + 
  geom_errorbar(data = data.mean, mapping = aes(x = Year, ymin = Incidence - Incidence.sd, ymax = Incidence + Incidence.sd, color = cmd)) + 
  
  # geom_line(data.mean, mapping = aes(x = Year, y = Incidence + Incidence.sd, color = cmd), 
  #   size = 1.0) + 
  # geom_line(data.mean, mapping = aes(x = Year, y = Incidence - Incidence.sd, color = cmd), 
  #   size = 1.0) + 
  #scale_y_continuous(limits = c(0.05,.22)) + 
  facet_wrap(scenario_name~ Gender, ncol=2) +
  xlab("Year")+ylab("") + 
  ggtitle("Incidence Rate by Depression Status") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(1990,2040,10)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p

```

### HIV Deaths

```{r}
 data <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>%
  filter(Year >= 1985, Year <=2025) %>% 
  group_by(Year, Gender, sim.ix, sim.id, scenario_name) %>% 
  summarize(Deaths = sum(Died_from_HIV * pop.scaling.factor), .groups = 'keep') %>%  
  ungroup() %>% 
  group_by(Year, Gender, sim.ix, sim.id, scenario_name) %>% 
  summarize(Deaths.sd = sd(Deaths), Deaths = mean(Deaths)) %>% 
  ungroup()# %>% 
  
p <- EMODAnalyzeR::emodplot.by_gender(data, 1990, 2025, 
                        "Deaths", title = "HIV deaths") 

p + #scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab("") + 
  scale_color_manual(values = c("blue","red","darkgreen","orange"))


# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/croi_HIV_deaths.pdf",
#       width = 8, height = 6, units = "in")
```

CROI measurement of deaths: Absolute and percent difference of new infections with and without coupling HIV together
```{r}
deaths.difference <- data %>% 
  pivot_wider(id_cols = c("Year", "Gender", "sim.ix"), names_from=c("scenario_name"), values_from = c("Deaths")) %>% 
  mutate(diff = baseline.art - decouple.art) %>% 
  group_by(sim.ix) %>% 
  summarize(diff = sum(diff), baseline.art = sum(baseline.art), decouple.art = sum(decouple.art)) %>% 
  mutate(pct.diff = diff/decouple.art) 
# %>% 
#   group_by(sim.ix) %>% 
#   summarize(diff = mean(diff), diff.sd = sd(diff),
#             pct.diff = mean(pct.diff), pct.diff.sd = sd(pct.diff),
#             baseline.art = mean(baseline.art), baseline.art.sd = sd(baseline.art),
#             decouple.art = mean(decouple.art), decouple.art.sd = sd(decouple.art))

(mean(deaths.difference$decouple.art) - mean(deaths.difference$baseline.art))/mean(deaths.difference$decouple.art) 


mean(deaths.difference$diff)

mean(deaths.difference$diff/deaths.difference$decouple.art)
sd(deaths.difference$diff/deaths.difference$decouple.art)

mean(deaths.difference$pct.diff)

sd(deaths.difference$pct.diff)


c(mean(deaths.difference$diff),
  lower_ci(mean(deaths.difference$diff), 
         sd(deaths.difference$diff)/sqrt(250),
         n = 250,
         conf_level = .95),
  upper_ci(mean(deaths.difference$diff), 
         sd(deaths.difference$diff)/sqrt(250),
         n = 250,
         conf_level = .95)
)


c(mean(deaths.difference$pct.diff),
  lower_ci(mean(deaths.difference$pct.diff), 
         sd(deaths.difference$pct.diff)/sqrt(250),
         n = 250,
         conf_level = .95),
  upper_ci(mean(deaths.difference$pct.diff), 
         sd(deaths.difference$pct.diff)/sqrt(250),
         n = 250,
         conf_level = .95)
)



```


```{r}
data %>% group_by(sim.ix, scenario_name) %>% summarise(Deaths = sum(Deaths)) %>% 
  group_by(scenario_name) %>% 
  summarize(Deaths.sd = sd(Deaths), Deaths = mean(Deaths))


c(659761.3	, lower_ci(659761.3	,65888.81	/sqrt(250), 250, .95), upper_ci(659761.3	,65888.81	/sqrt(250), 250, .95))
```

## Depression Prevalence over time
```{r, fig.width=8, fig.height=8}
data.cmd <- sim.results.all %>% filter(Age > 18) %>% 
  mutate(HIVneg = Population - Infected) %>% 
  group_by(Year, Gender, sim.id, IP_Key.CMDStatus, scenario_name) %>% 
  summarize(Population = sum(Population),
            HIVneg = sum(HIVneg),
            Infected = sum(Infected), .groups = 'keep') %>% 
  ungroup() %>% 
  pivot_wider(id_cols = c(Year, Gender, sim.id, scenario_name),
              names_from = c(IP_Key.CMDStatus),
              values_from = c(Population, HIVneg, Infected))  %>% 
  mutate(Population_total = Population_CMD_pos + Population_CMD_neg + Population_CMD_recovered + Population_CMD_treated,
         HIVneg_total = HIVneg_CMD_pos + HIVneg_CMD_neg + HIVneg_CMD_recovered + HIVneg_CMD_treated,
         Infected_total = Infected_CMD_pos + Infected_CMD_neg + Infected_CMD_recovered + Infected_CMD_treated) %>% 
  mutate(CMD_prev_overall = case_when(Population_total == 0 ~ 0,
                                    Population_total > 0 ~ Population_CMD_pos/Population_total),
         CMD_prev_HIVneg = case_when(HIVneg_total == 0 ~ 0,
                                    HIVneg_total > 0 ~ HIVneg_CMD_pos/HIVneg_total),
         CMD_prev_Infected = case_when(Infected_total == 0 ~ 0,
                                    Infected_total > 0 ~ Infected_CMD_pos/Infected_total)) %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

data.cmd.mean <- data.cmd %>% 
  group_by(Year, Gender, scenario_name) %>%
  summarize(Overall = mean(CMD_prev_overall), Overall_sd = sd(CMD_prev_overall),
            HIVneg = mean(CMD_prev_HIVneg), HIVneg_sd = sd(CMD_prev_HIVneg),
            Infected = mean(CMD_prev_Infected), Infected_sd = sd(CMD_prev_Infected),
            .groups = "keep") %>% 
  ungroup()

# Plot  
p = ggplot() +
  geom_line( data = data.cmd.mean %>% 
                    select(Year, Gender, Overall, Infected, HIVneg, scenario_name) %>% 
                    pivot_longer(cols = c(Overall, Infected, HIVneg),
                                 names_to = "Depression.Prevalence", 
                                 values_to = "CMD_prev"),
    mapping = aes(x = Year, y = CMD_prev, color = Depression.Prevalence), 
    size = 1.0) + 
  scale_y_continuous(limits = c(0.05,.22)) + 
  facet_wrap(scenario_name ~ Gender, ncol=2) +
  xlab("Year")+ylab("") + 
  ggtitle("Depression Prevalence by HIV status") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(1980,2040,10)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/croi_depression_prev.pdf",
       width = 8, height = 8, units = "in")
```

## Depression Age-Prevalence Curves

In 2004, the year of the WHO health survey in Kenya
```{r}
obs.cmdprev.sheet <- data.frame(Year = 2004, 
           Gender = c("Male", "Male", "Male", "Male", "Male", "Male", "Male", 
                    "Female", "Female", "Female", "Female", "Female", "Female", "Female"),
           AgeBin =  c("[18:24)", "[25:29)", "[30:39)", "[40:44)", "[45:49)", "[50:59)", "[60:99)",
                      "[18:24)", "[25:29)", "[30:39)", "[40:44)", "[45:49)", "[50:59)", "[60:99)"),
           CMDPrevalence = c(0.03, 0.069, 0.098, 0.087, 0.11, 0.13, 0.2, 
                             0.065, 0.086, 0.067, 0.12, 0.13, 0.079, 0.051)
)
obs.cmdprev.sheet$AgeBin_index = factor(obs.cmdprev.sheet$AgeBin,labels = 1:7)
```



```{r, fig.height=8, fig.width =8}
cmd.data.age <- sim.results.all %>% 
  filter(Age > 18) %>% 
  filter(Year %in% c(2004)) %>% 
  mutate(HIVneg = Population - Infected) %>% 
  group_by(Year, Gender, Age, sim.id, IP_Key.CMDStatus, scenario_name) %>% 
  summarize(Population = sum(Population),
            HIVneg = sum(HIVneg),
            Infected = sum(Infected), .groups = 'keep') %>% 
  ungroup() %>% 
  pivot_wider(id_cols = c(Year, Gender, Age, sim.id, scenario_name),
              names_from = c(IP_Key.CMDStatus),
              values_from = c(Population, HIVneg, Infected))  %>% 
  mutate(Population_total = Population_CMD_pos + Population_CMD_neg + Population_CMD_recovered + Population_CMD_treated,
         HIVneg_total = HIVneg_CMD_pos + HIVneg_CMD_neg + HIVneg_CMD_recovered + HIVneg_CMD_treated,
         Infected_total = Infected_CMD_pos + Infected_CMD_neg + Infected_CMD_recovered + Infected_CMD_treated) %>% 
  mutate(CMD_prev_overall = case_when(Population_total == 0 ~ 0,
                                    Population_total > 0 ~ Population_CMD_pos/Population_total),
         CMD_prev_HIVneg = case_when(HIVneg_total == 0 ~ 0,
                                    HIVneg_total > 0 ~ HIVneg_CMD_pos/HIVneg_total),
         CMD_prev_Infected = case_when(Infected_total == 0 ~ 0,
                                    Infected_total > 0 ~ Infected_CMD_pos/Infected_total)) %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

# Define age bins
age_bins = c(18, 25, 30, 40, 45, 50, 60, 99)
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
cmd.data.age <- cmd.data.age %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
cmd.data.age$AgeBin_index = factor(cmd.data.age$AgeBin,labels = 1:length(age_labels))

cmd.data.age.mean <- cmd.data.age %>% 
  group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>% 
  summarize(mean.Overall = mean(CMD_prev_overall), sd.Overall = sd(CMD_prev_overall),
            mean.HIVneg = mean(CMD_prev_HIVneg), sd.HIVneg = sd(CMD_prev_HIVneg),
            mean.Infected = mean(CMD_prev_Infected), sd.Infected = sd(CMD_prev_Infected),
              .groups = 'keep') %>% 
  mutate(lb.Overall = max(mean.Overall - 2* sd.Overall, 0), ub.Overall = mean.Overall + 2*sd.Overall,
         lb.HIVneg = max(mean.HIVneg - 2* sd.HIVneg, 0), ub.HIVneg = mean.HIVneg + 2*sd.HIVneg,
         lb.Infected = max(mean.Infected - 2* sd.Infected, 0), ub.Infected = mean.Infected + 2*sd.Infected
)

p <- cmd.data.age.mean %>% 
  ggplot() + 
  geom_point(mapping = aes(x = AgeBin_index, y = mean.Overall), 
             size = 2, color = 'darkgreen') + 
  geom_errorbar(mapping = aes(x = AgeBin_index, ymin = lb.Overall, ymax = ub.Overall),
                width = .3, size =2, color = 'darkgreen') + 
  facet_grid(cols = vars(Gender), rows = vars(scenario_name)) + 
  xlab("Age") + ylab("") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    ) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p + 
  geom_point(obs.cmdprev.sheet,
             mapping = aes(x = AgeBin_index, y = CMDPrevalence), color = 'orange', size = 3) + 
  ylab("Depression Prevalence by Age")

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/croi_depression_age_prev.pdf",
#        width = 8, height = 8, units = "in")

```


```{r}
cmd.data.age.mean %>% 
  filter(scenario_name == "minimal",
         Gender == "Male", Year == 2004) %>% 
  select("Year" ,"AgeBin_index", "AgeBin", "Gender", "mean.Infected", "mean.HIVneg"
)

cmd.data.age.mean %>% 
  filter(scenario_name == "minimal",
         Gender == "Female") %>% 
  select("Year" ,"AgeBin_index", "AgeBin", "Gender", "mean.Infected", "mean.HIVneg"
)
```

# CROI measurements - ART Benefit

## Cases averted

```{r}
data <- sim.results.all %>%
  #mutate(Year = ceiling(Year)) %>% 
  filter(Year >= 1985, Year <=2025) %>% 
  group_by(sim.ix, scenario_name) %>% 
  summarize(NewInf = sum(Newly.Infected * pop.scaling.factor), 
            OnART = sum(On_ART * pop.scaling.factor), # factor of 2 to avoid double counting
            .groups = 'keep')

# Deaths averted by lookign at difference between art and no art - baseline

art.benefit <- data %>% 
  pivot_wider(id_cols = c("sim.ix"), names_from=c("scenario_name"), values_from = c("NewInf", "OnART")) %>% 
  # This is the number of deaths averted
  # deaths is higher without ART, should be positive
  mutate(baseline.averted = NewInf_baseline.noart - NewInf_baseline.art, 
         decouple.averted = NewInf_decouple.noart - NewInf_decouple.art) %>% 
  # rescale each of these by the number of person-years on ART
  mutate(baseline.averted.rescale = baseline.averted/OnART_baseline.art,
         decouple.averted.rescale = decouple.averted/OnART_decouple.art) %>% 
  # find the difference in ART benefit, and the percent difference 
  mutate(averted.difference = baseline.averted.rescale - decouple.averted.rescale,
         averted.pct = (baseline.averted.rescale - decouple.averted.rescale)/decouple.averted.rescale) 


c(art.benefit$baseline.averted %>% mean,
  art.benefit$decouple.averted %>% mean)

c(art.benefit$averted.difference %>% mean,
  art.benefit$averted.difference %>% sd,
  art.benefit$averted.pct %>% mean,
  art.benefit$averted.pct %>% sd)
```


## HIV deaths averted

```{r}
data <- sim.results.all %>%
  #mutate(Year = ceiling(Year)) %>% 
  filter(Year >= 1985, Year <=2025) %>% 
  group_by(sim.ix, scenario_name) %>% 
  summarize(Deaths = sum(Died_from_HIV * pop.scaling.factor), 
  #summarize(Deaths = sum(Died_from_HIV/Infected * pop.scaling.factor), 
            OnART = sum(On_ART/2 * pop.scaling.factor), # factor of 2 to avoid double counting
            PLHIV = sum(Infected/2 * pop.scaling.factor),
            .groups = 'keep')
```

Deaths Averted

```{r}
art.benefit <- data %>% 
  pivot_wider(id_cols = c("sim.ix"), names_from=c("scenario_name"), values_from = c("Deaths", "OnART", "PLHIV")) %>% 
  # This is the number of deaths averted
  # deaths is higher without ART, should be positive
  mutate(baseline.averted = Deaths_baseline.noart - Deaths_baseline.art, 
         decouple.averted = Deaths_decouple.noart - Deaths_decouple.art) %>% 
  # find the difference in ART benefit, and the percent difference 
  # we expect that ART benefit is *smaller* if people are depressed
  mutate(averted.difference = baseline.averted - decouple.averted,
         averted.pct = (baseline.averted - decouple.averted)/decouple.averted) 

art.benefit %>% 
  ungroup() %>% 
  summarize(averted.difference = mean(averted.difference),
            averted.pct = mean(averted.pct))

```


Deaths Averted per person-year of living with HIV

```{r}


# Deaths averted by lookign at difference between art and no art - baseline

art.benefit <- data %>% 
  pivot_wider(id_cols = c("sim.ix"), names_from=c("scenario_name"), values_from = c("Deaths", "OnART", "PLHIV")) %>% 
  # This is the number of deaths averted
  # deaths is higher without ART, should be positive
  mutate(baseline.averted = Deaths_baseline.noart - Deaths_baseline.art, 
         decouple.averted = Deaths_decouple.noart - Deaths_decouple.art) %>% 
  # rescale each of these by the number of person-years on ART
  # mutate(baseline.averted.rescale = baseline.averted/OnART_baseline.art,
  #        decouple.averted.rescale = decouple.averted/OnART_decouple.art) %>% 
  mutate(baseline.averted.rescale = baseline.averted/PLHIV_baseline.art, 
         decouple.averted.rescale = decouple.averted/PLHIV_decouple.art) %>% 
  # find the difference in ART benefit, and the percent difference 
  mutate(averted.difference = baseline.averted.rescale - decouple.averted.rescale,
         averted.pct = (baseline.averted.rescale - decouple.averted.rescale)/decouple.averted.rescale) 


art.benefit %>% 
  ungroup() %>% 
  summarize(
    averted.difference.sd = sd(averted.difference),
    averted.difference = mean(averted.difference),
    averted.pct.sd = sd(averted.pct),
    averted.pct = mean(averted.pct))


```


Deaths Averted per person-year of living with ART

```{r}


# Deaths averted by lookign at difference between art and no art - baseline

art.benefit <- data %>% 
  pivot_wider(id_cols = c("sim.ix"), names_from=c("scenario_name"), values_from = c("Deaths", "OnART", "PLHIV")) %>% 
  # This is the number of deaths averted
  # deaths is higher without ART, should be positive
  mutate(baseline.averted = Deaths_baseline.noart - Deaths_baseline.art, 
         decouple.averted = Deaths_decouple.noart - Deaths_decouple.art) %>% 
  # rescale each of these by the number of person-years on ART
  # mutate(baseline.averted.rescale = baseline.averted/OnART_baseline.art,
  #        decouple.averted.rescale = decouple.averted/OnART_decouple.art) %>% 
  mutate(baseline.averted.rescale = baseline.averted/OnART_baseline.art, 
         decouple.averted.rescale = decouple.averted/OnART_baseline.art) %>% 
  # find the difference in ART benefit, and the percent difference 
  mutate(averted.difference = baseline.averted.rescale - decouple.averted.rescale,
         averted.pct = (baseline.averted.rescale - decouple.averted.rescale)/decouple.averted.rescale) 

art.benefit %>% 
  ungroup() %>% 
  summarize(
    averted.difference.sd = sd(averted.difference),
    averted.difference = mean(averted.difference),
    averted.pct.sd = sd(averted.pct),
    averted.pct = mean(averted.pct))

```

Mortality rate, HIV deaths per PLHIV plot over time

```{r}
sim.results.all %>% colnames

# calculate death rate in each year, in each simulation
sim.results.all %>% 
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(Infected = sum(Infected * pop.scaling.factor),
            Died_from_HIV = sum(Died_from_HIV * pop.scaling.factor)) %>% 
  ungroup() %>%  
  mutate(mort.rate = case_when(Infected == 0 ~ 0, 
                               Infected > 0 ~ Died_from_HIV/Infected)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(mort.rate = mean(mort.rate)) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = mort.rate, color = scenario_name)) 
  
  

```


```{r}
c(
  art.benefit$averted.pct,
  lower_ci(art.benefit$averted.pct, art.benefit$averted.pct.sd/sqrt(250), 250, .95), 
  upper_ci(art.benefit$averted.pct, art.benefit$averted.pct.sd/sqrt(250), 250, .95)
)

c(
  art.benefit$averted.diff,
  lower_ci(art.benefit$averted.diff, art.benefit$averted.diff.sd/sqrt(250), 250, .95), 
  upper_ci(art.benefit$averted.diff, art.benefit$averted.diff.sd/sqrt(250), 250, .95)
)
```
```{r}
sim.results.all %>% filter(sim.ix == 1) %>% 
  filter(Year == ceiling(Year)) %>% 
  group_by(scenario_name, sim.ix) %>% 
  summarize(On_ART = sum(On_ART))
```

## Depression episodes averted

Try just counting people who are depressed, say it happens once per year per person:
```{r}
data <- sim.results.all %>% 
  #mutate(Year = ceiling(Year)) %>% 
  filter(Year >= 1985, Year <=2025,
         IP_Key.CMDStatus == "CMD_pos") %>% 
  group_by(sim.ix, scenario_name) %>% 
  summarize(deps = sum(Population * pop.scaling.factor), 
  #summarize(Deaths = sum(Died_from_HIV/Infected * pop.scaling.factor), 
            .groups = 'keep')

  pivot_wider(id_cols = c("Year", "Gender", "sim.ix"), names_from=c("scenario_name"), values_from = c("NewCases")) %>% 
  mutate(diff = baseline.art - decouple.art) %>% 
  group_by(sim.ix) %>% 
  summarize(diff = sum(diff), baseline.art = sum(baseline.art), decouple.art = sum(decouple.art)) %>% 
  mutate(pct.diff = diff/decouple.art) 

dep.eps <- data %>% 
  pivot_wider(id_cols = c("sim.ix"), names_from=c("scenario_name"), values_from = c("deps")) %>% 
  mutate(diff = baseline.art - decouple.art) %>% 
  group_by(sim.ix) %>% 
  summarize(diff = sum(diff), baseline.art = sum(baseline.art), decouple.art = sum(decouple.art)) %>% 
  mutate(pct.diff = diff/decouple.art) 
  
dep.stat <- dep.eps %>% 
  ungroup() %>% 
  summarize(diff.sd = sd(diff),
            diff = mean(diff),
            pct.sd = sd(pct.diff),
            pct.diff = mean(pct.diff))

dep.stat
```

```{r}
c(mean(dep.eps$pct.diff),
  lower_ci(mean(dep.eps$pct.diff), 
         sd(dep.eps$pct.diff)/sqrt(250),
         n = 250,
         conf_level = .95),
  upper_ci(mean(dep.eps$pct.diff), 
         sd(dep.eps$pct.diff)/sqrt(250),
         n = 250,
         conf_level = .95)
)

```

```{r}
data %>% group_by(sim.ix, scenario_name) %>% summarise(deps = sum(deps)) %>% 
  group_by(scenario_name) %>% 
  summarize(deps.sd = sd(deps), deps = mean(deps))

c(17691275	, lower_ci(17691275	,124847.12		/sqrt(250), 250, .95), upper_ci(17691275	,124847.12		/sqrt(250), 250, .95))
```

## DALYs averted