---
title: "debugging_cmdinc"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The purpose of this notebook is to more carefully and rigorously debug the CMDINC intervention in EMOD.

WHAT IT IS: CMDINC is an intervention where PLHIV experience higher rates of HIV incidence

WHAT IS WRONG WITH IT: when we turn it on, key HIV outcomes - incidence and deaths - go down. There is somehow less HIV when we have more depression, even though there is no other interaction between depression and HIV.

DIAGNOSIS: 

* Clearly, this can't be the case; it must be that there is some other interaction between HIV and depression turned on in the simulation that makes it so that when there is more depression there also results in a change to HIV outcomes. On average, the really shouldn't lead to any substantial differences between CMDINC and fully decoupled model, especially prior to 1990 when ART begins.

PROCEDURE: I am going to remove ALL of the interactions between HIV and depression except for CMDINC and compare the CMDINC model against the fully decoupled model. Then I am going to put back in each of the interactions one by one until I start to see major discrepancies. This is a "Hello World!" approach to debugging an extremely complicated dynamical model.

1. Absolute bare bones decouple vs. CMDINC
2. Restore delays to diagnosis
3. Restore art adherence
4. Restore differential ART dropout times calculated at time of ART initiation
5. Recalculate ART dropout times when CMD status changes while on ART

METRICS: I am going to look at the differences between CMDINC and the decoupled model

## Initialize libraries and functions

```{r Load Libraries}
library(tidyverse)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
library(readxl)
devtools::install_github("BershteynLab/EMODAnalyzeR", force = TRUE)
```


```{r}
# Confidence interval functions
lower_ci <- function(mean, se, n, conf_level = 0.95){
  lower_ci <- mean - qt(1 - ((1 - conf_level) / 2), n - 1) * se
  return(lower_ci)
}
upper_ci <- function(mean, se, n, conf_level = 0.95){
  upper_ci <- mean + qt(1 - ((1 - conf_level) / 2), n - 1) * se
  return(upper_ci)
}
```

# Read in Data

## Hello World
```{r}
# 1960-2020 using hello world
experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-baseline_art_cmdinc_test_helloworld___2024_04_23_18_29_38_731319"

sim.results.cmdinc <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path,
  scenario_name = 'cmdinc',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# 1960-2020 using hello world
experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-decouple_art_test_helloworld___2024_04_23_18_32_12_699193"

sim.results.decouple <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path,
  scenario_name = 'decouple',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

```

## Putting back in delay to diagnosis
```{r}
# CMDINC
experiment_path.delay = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-baseline_art_cmdinc_test_helloworld___2024_04_24_14_53_35_336366"

sim.results.cmdinc.delay <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.delay,
  scenario_name = 'cmdinc.delay',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Decouple
experiment_path.delay = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-decouple_art_test_helloworld___2024_04_24_14_55_56_088033"

sim.results.decouple.delay <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.delay,
  scenario_name = 'decouple.delay',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

```

## Putting back in art adherence
```{r}
# CMDINC
experiment_path.delay.adh = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-baseline_art_cmdinc_test_helloworld___2024_04_24_21_15_08_905770"

sim.results.cmdinc.delay.adh <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.delay.adh,
  scenario_name = 'cmdinc.delay.adh',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Decouple
experiment_path.delay.adh = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-decouple_art_test_helloworld___2024_04_24_21_17_26_424609"

sim.results.decouple.delay.adh <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.delay.adh,
  scenario_name = 'decouple.delay.adh',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)
```

## Putting back in delay to ART dropout - calculated at time of ART initiation
```{r}
# CMDINC
experiment_path.dropout1 = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-baseline_art_cmdinc_test_helloworld___2024_04_26_12_11_44_035581"

sim.results.cmdinc.delay.adh.dropout1 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.dropout1,
  scenario_name = 'cmdinc.delay.adh.dropout1',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Decouple
experiment_path.dropout1 = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-decouple_art_test_helloworld___2024_04_26_12_14_22_055171"

sim.results.decouple.delay.adh.dropout1 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.dropout1,
  scenario_name = 'decouple.delay.adh.dropout1',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)
```

## Adding recalculation ART dropout upon switching CMD status

```{r}

# CMDINC
experiment_path.dropout2 = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-baseline_art_cmdinc_test_helloworld___2024_04_26_13_45_31_841017"

sim.results.cmdinc.delay.adh.dropout2 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.dropout2,
  scenario_name = 'cmdinc.delay.adh.dropout2',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Decouple
experiment_path.dropout2 = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-decouple_art_test_helloworld___2024_04_26_13_47_50_726968"

sim.results.decouple.delay.adh.dropout2 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.dropout2,
  scenario_name = 'decouple.delay.adh.dropout2',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)
```


## Adding ART status change upon switching CMD status

```{r}

# CMDINC
#experiment_path.artswitch = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-baseline_art_cmdinc_test_helloworld___2024_04_26_19_21_22_297654"
#experiment_path.artswitch = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-baseline_art_cmdinc_test_helloworld___2024_04_26_23_13_23_491256"
#experiment_path.artswitch = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-baseline_art_cmdinc_test_helloworld___2024_04_27_13_46_18_860232"
# switching on and off
# experiment_path.artswitch = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-baseline_art_cmdinc_test_helloworld___2024_04_27_22_56_00_832523"

# brand new art switching action
#experiment_path.artswitch = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-artswitch___2024_05_03_11_45_24_723135"
experiment_path.artswitch.on = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_test_helloworld-artswitch_on___2024_05_05_19_59_23_236963"
sim.results.cmdinc.delay.adh.dropout2.artswitch.on <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.artswitch.on,
  scenario_name = 'cmdinc.delay.adh.dropout2.artswitch',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Decouple
#experiment_path.artswitch = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-decouple_art_test_helloworld___2024_04_26_19_23_49_117978"

# old version of art switch
#experiment_path.artswitch =  "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-decouple_art_test_helloworld___2024_04_26_23_15_56_174258"
# new version of art switch
#experiment_path.artswitch = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-decouple_art_test_helloworld___2024_04_27_13_48_45_250204"
# switching on and off
#experiment_path.artswitch = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-decouple_art_test_helloworld___2024_04_27_22_58_28_726370"

# brand new art switching action
experiment_path.artswitch.on = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-artswitch___2024_05_03_11_47_57_792384"


sim.results.decouple.delay.adh.dropout2.artswitch.on <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.artswitch.on,
  scenario_name = 'decouple.delay.adh.dropout2.artswitch',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

## Turning off art switching - sanity check
experiment_path.artswitch.off = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_decouple_test_helloworld-artswitch_off___2024_05_05_20_15_11_137933"

sim.results.decouple.delay.adh.dropout2.artswitch.off <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment_path.artswitch.off,
  scenario_name = 'decouple.delay.adh.dropout2.artswitch',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  #stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  stratify_columns = c("Year", "Gender","IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)
```


# Combine data

```{r}
sim.results.all <- rbind(sim.results.decouple,
                         sim.results.cmdinc,
                         sim.results.decouple.delay,
                         sim.results.cmdinc.delay,
                         sim.results.decouple.delay.adh,
                         sim.results.cmdinc.delay.adh,
                         sim.results.decouple.delay.adh.dropout1,
                         sim.results.cmdinc.delay.adh.dropout1,
                         sim.results.decouple.delay.adh.dropout2,
                         sim.results.cmdinc.delay.adh.dropout2,
                         sim.results.decouple.delay.adh.dropout2.artswitch.on,
                         sim.results.cmdinc.delay.adh.dropout2.artswitch.on,
                         sim.results.decouple.delay.adh.dropout2.artswitch.off
                         )
```

## Rescaling

```{r}
CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.all %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.ix, scenario_name) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.all <- sim.results.all %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )
```

# Analysis

```{r}
test.comparison <- sim.results.all %>%
 group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(Population = sum(Population), 
            Infected = sum(Infected ),
            Died = sum(Died  ),
            Died_from_HIV = sum(Died_from_HIV  ),
            Newly.Infected = sum(Newly.Infected )) %>% ungroup()

test.comp.mean <- test.comparison %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(Population = mean(Population), 
            Infected = mean(Infected),
            Died = mean(Died),
            Died_from_HIV = mean(Died_from_HIV),
            Newly.Infected = mean(Newly.Infected)) %>% ungroup()
```

Check individual trajectories:

```{r}
test.comparison %>% 
  filter(sim.ix == 1) %>% arrange(Gender, Year, scenario_name) %>% View
```

## Check aggregated mean:

### 1980-1990 (pre=art)
```{r}
test.comp.mean %>% arrange(Year, Gender, scenario_name) %>% 
  filter(Year >= 1980, Year < 1990) %>% 
  group_by(Gender, scenario_name) %>% 
  summarize(Infected = sum(Infected),
           Died_from_HIV = sum(Died_from_HIV),
           Newly.Infected = sum(Newly.Infected)) %>% head(24)

```

### 1990-2000 (pre-art)
```{r}
test.comp.mean %>% arrange(Year, Gender, scenario_name) %>% 
  filter(Year >= 1990, Year < 2000) %>% 
  group_by(Gender, scenario_name) %>% 
  summarize(Infected = sum(Infected),
           Died_from_HIV = sum(Died_from_HIV),
           Newly.Infected = sum(Newly.Infected))
```

### 2000-2020 (ART)
```{r}
test.comp.mean %>% arrange(Year, Gender, scenario_name) %>% 
  filter(Year >= 2000, Year < 2020) %>% 
  group_by(Gender, scenario_name) %>% 
  summarize(Infected = sum(Infected),
           Died_from_HIV = sum(Died_from_HIV),
           Newly.Infected = sum(Newly.Infected))
```

## Calculate totals with error bars

```{r}
start_year = 1980
end_year = 2021
nruns = 250
```

```{r}
sim.results.all.agg <- sim.results.all %>% 
  filter(Year >= start_year, Year < end_year)  %>% 
  group_by(Gender, scenario_name, sim.ix) %>% 
  summarize(Newly.Infected = sum(Newly.Infected), # * pop.scaling.factor), 
            Died_from_HIV = sum(Died_from_HIV), # * pop.scaling.factor),
            Depression.eps = sum(Died), # sum(Population/2),# * pop.scaling.factor),
            .groups = 'keep') %>%
  ungroup() 

sim.results.all.agg.numbers <- sim.results.all.agg %>% 
  group_by(Gender, scenario_name) %>% 
  summarize(
    Newly.Infected.sd = sd(Newly.Infected),
    Newly.Infected = mean(Newly.Infected), 
    Died_from_HIV.sd = sd(Died_from_HIV),
    Died_from_HIV = mean(Died_from_HIV),
    Depression.eps.sd = sd(Depression.eps),
    Depression.eps = mean(Depression.eps), .groups = "keep") %>% 
  ungroup() %>% 
  mutate(
    Newly.Infected_95LL = lower_ci(Newly.Infected, Newly.Infected.sd/sqrt(nruns), nruns, conf_level = .95),
    Newly.Infected_95UL = upper_ci(Newly.Infected, Newly.Infected.sd/sqrt(nruns), nruns, conf_level = .95),
    Died_from_HIV_95LL = lower_ci(Died_from_HIV, Died_from_HIV.sd/sqrt(nruns), nruns, conf_level = .95),
    Died_from_HIV_95UL = upper_ci(Died_from_HIV, Died_from_HIV.sd/sqrt(nruns), nruns, conf_level = .95),
    Depression.eps_95LL = lower_ci(Depression.eps, Depression.eps.sd/sqrt(nruns), nruns, conf_level = .95),
    Depression.eps_95UL = upper_ci(Depression.eps, Depression.eps.sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(
    "Gender", "scenario_name",
    "Newly.Infected", "Newly.Infected.sd", "Newly.Infected_95LL","Newly.Infected_95UL",
    "Died_from_HIV", "Died_from_HIV.sd", "Died_from_HIV_95LL", "Died_from_HIV_95UL",
    "Depression.eps", "Depression.eps.sd", "Depression.eps_95LL", "Depression.eps_95UL"
  ) %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

sim.results.all.agg.numbers

```

```{r}
ggplot(data = sim.results.all.agg.numbers) + 
  geom_point(mapping = aes(x = scenario_name, y = Newly.Infected, color = Gender)) + 
  geom_errorbar(aes(x=scenario_name, ymin = Newly.Infected_95LL, ymax = Newly.Infected_95UL)) + 
  facet_wrap(~ Gender, ncol=2) + 
  scale_color_manual(values = c("red", "blue"))  + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```

```{r}
ggplot(data = sim.results.all.agg.numbers) + 
  geom_point(mapping = aes(x = scenario_name, y = Died_from_HIV, color = Gender)) + 
  geom_errorbar(aes(x=scenario_name, ymin = Died_from_HIV_95LL, ymax = Died_from_HIV_95UL)) + 
  facet_wrap(~ Gender, ncol=2) + 
  scale_color_manual(values = c("red", "blue"))  + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```

## Calculate differences
```{r}
sim.results.all.agg.differences = sim.results.all.agg %>% 
  filter(scenario_name == "decouple") %>% 
  select(Gender, sim.ix, 
         Newly.Infected.Decouple = Newly.Infected,
         Died_from_HIV.Decouple = Died_from_HIV,
         Depression.eps.Decouple = Depression.eps
         ) %>%
  merge(sim.results.all.agg,
        by = c("Gender", "sim.ix")) %>%
  mutate(
    Newly.Infected.diff = Newly.Infected - Newly.Infected.Decouple,
    Newly.Infected.pct = (Newly.Infected - Newly.Infected.Decouple)/Newly.Infected.Decouple,
    Died_from_HIV.diff = Died_from_HIV - Died_from_HIV.Decouple,
    Died_from_HIV.pct = (Died_from_HIV - Died_from_HIV.Decouple)/Died_from_HIV.Decouple,
    Depression.eps.diff = Depression.eps - Depression.eps.Decouple,
    Depression.eps.pct = (Depression.eps - Depression.eps.Decouple)/Depression.eps.Decouple,
) %>% 
  group_by(Gender, scenario_name) %>% 
  summarize(Newly.Infected.diff.sd = sd(Newly.Infected.diff),
            Newly.Infected.diff = mean(Newly.Infected.diff),
            Newly.Infected.pct.sd = sd(Newly.Infected.pct),
            Newly.Infected.pct = mean(Newly.Infected.pct),
            Died_from_HIV.diff.sd = sd(Died_from_HIV.diff),
            Died_from_HIV.diff = mean(Died_from_HIV.diff),
            Died_from_HIV.pct.sd = sd(Died_from_HIV.pct),
            Died_from_HIV.pct = mean(Died_from_HIV.pct),
            Depression.eps.diff.sd = sd(Depression.eps.diff),
            Depression.eps.diff = mean(Depression.eps.diff),
            Depression.eps.pct.sd = sd(Depression.eps.pct),
            Depression.eps.pct = mean(Depression.eps.pct), .groups = 'keep'
            ) %>% 
  ungroup() %>% 
  mutate(
    Newly.Infected.diff_95LL = lower_ci(Newly.Infected.diff, Newly.Infected.diff.sd/sqrt(nruns), nruns, conf_level = .95),
    Newly.Infected.diff_95UL = upper_ci(Newly.Infected.diff, Newly.Infected.diff.sd/sqrt(nruns), nruns, conf_level = .95),
    Newly.Infected.pct_95LL = lower_ci(Newly.Infected.pct, Newly.Infected.pct.sd/sqrt(nruns), nruns, conf_level = .95),
    Newly.Infected.pct_95UL = upper_ci(Newly.Infected.pct, Newly.Infected.pct.sd/sqrt(nruns), nruns, conf_level = .95),
    Died_from_HIV.diff_95LL = lower_ci(Died_from_HIV.diff, Died_from_HIV.diff.sd/sqrt(nruns), nruns, conf_level = .95),
    Died_from_HIV.diff_95UL = upper_ci(Died_from_HIV.diff, Died_from_HIV.diff.sd/sqrt(nruns), nruns, conf_level = .95),
    Died_from_HIV.pct_95LL = lower_ci(Died_from_HIV.pct, Died_from_HIV.pct.sd/sqrt(nruns), nruns, conf_level = .95),
    Died_from_HIV.pct_95UL = upper_ci(Died_from_HIV.pct, Died_from_HIV.pct.sd/sqrt(nruns), nruns, conf_level = .95),
    Depression.eps.diff_95LL = lower_ci(Depression.eps.diff, Depression.eps.diff.sd/sqrt(nruns), nruns, conf_level = .95),
    Depression.eps.diff_95UL = upper_ci(Depression.eps.diff, Depression.eps.diff.sd/sqrt(nruns), nruns, conf_level = .95),
    Depression.eps.pct_95LL = lower_ci(Depression.eps.pct, Depression.eps.pct.sd/sqrt(nruns), nruns, conf_level = .95),
    Depression.eps.pct_95UL = upper_ci(Depression.eps.pct, Depression.eps.pct.sd/sqrt(nruns), nruns, conf_level = .95) 
  )  %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>% 
  select(
    "Gender", "scenario_name",
    "Newly.Infected.diff", "Newly.Infected.diff.sd", "Newly.Infected.diff_95LL","Newly.Infected.diff_95UL",
    "Newly.Infected.pct" ,"Newly.Infected.pct.sd" , "Newly.Infected.pct_95LL",  "Newly.Infected.pct_95UL",
    "Died_from_HIV.diff", "Died_from_HIV.diff.sd", "Died_from_HIV.diff_95LL", "Died_from_HIV.diff_95UL",
    "Died_from_HIV.pct", "Died_from_HIV.pct.sd", "Died_from_HIV.pct_95LL", "Died_from_HIV.pct_95UL",
    "Depression.eps.diff", "Depression.eps.diff.sd", "Depression.eps.diff_95LL", "Depression.eps.diff_95UL",
    "Depression.eps.pct", "Depression.eps.pct.sd", "Depression.eps.pct_95LL", "Depression.eps.pct_95UL"
  )

sim.results.all.agg.differences
```


```{r}
ggplot(data = sim.results.all.agg.differences) + 
  geom_point(mapping = aes(x = scenario_name, y = Newly.Infected.diff, color = Gender)) + 
  geom_errorbar(aes(x=scenario_name, ymin = Newly.Infected.diff_95LL, ymax = Newly.Infected.diff_95UL)) + 
  facet_wrap(~ Gender, ncol=2) + 
  scale_color_manual(values = c("red", "blue"))  + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```

```{r}
ggplot(data = sim.results.all.agg.differences) + 
  geom_point(mapping = aes(x = scenario_name, y = Newly.Infected.pct, color = Gender)) + 
  geom_errorbar(aes(x=scenario_name, ymin = Newly.Infected.pct_95LL, ymax = Newly.Infected.pct_95UL)) + 
  facet_wrap(~ Gender, ncol=2) + 
  scale_color_manual(values = c("red", "blue"))  + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```

```{r}
ggplot(data = sim.results.all.agg.differences) + 
  geom_point(mapping = aes(x = scenario_name, y = Died_from_HIV.diff, color = Gender)) + 
  geom_errorbar(aes(x=scenario_name, ymin = Died_from_HIV.diff_95LL, ymax = Died_from_HIV.diff_95UL)) + 
  facet_wrap(~ Gender, ncol=2) + 
  scale_color_manual(values = c("red", "blue"))  + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```

```{r}
ggplot(data = sim.results.all.agg.differences) + 
  geom_point(mapping = aes(x = scenario_name, y = Died_from_HIV.pct, color = Gender)) + 
  geom_errorbar(aes(x=scenario_name, ymin = Died_from_HIV.pct_95LL, ymax = Died_from_HIV.pct_95UL)) + 
  facet_wrap(~ Gender, ncol=2) + 
  scale_color_manual(values = c("red", "blue"))  + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```

