---
title: "impact_manuscript_analysis"
output: html_document
date: "2024-12-12"
---

# Introduction

The purpose of this notebook is exploratory analysis for the upcoming impact of
depression treatment on HIV outcomes manuscript

# Libraries

```{r Load Libraries, echo = FALSE}
library(tidyverse)
library(data.table)
library(magrittr)
library(rsample)
library(readxl)
library(devtools)
library(ggpubr)
library(patchwork)

devtools::install_github("BershteynLab/EMODAnalyzeR", force = TRUE)
```

# Checking results

There was a strange error with distribution in the status neutral HIV scenario, 
conducted in October of 2024 in preparation for the now-rejected CROI 2025 abstract.

Somehow, status neutral depression care wasn't being distributed at the expected scale.

Let's first compare and contract the two ways that distribution occurred:

## Baseline

```{r}
#experiment.path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/CROI2025/Baseline-campaign_MATUMAINI_202305-baseline___2024_09_23_12_05_01_062691"
experiment.path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/CROI2025/Baseline-campaign_MATUMAINI_202305-baseline___2024_09_23_17_43_09_994878"
sim.results.baseline <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name = "baseline",
    summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus", "CMD_Treat_staging", "CMD_Treat"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)
```

## Universal treatment data
```{r}
#experiment.path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/CRaOI2025/Baseline-campaign_MATUMAINI_202305_uni-uni___2024_09_23_12_26_37_798115"
experiment.path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/CROI2025/Baseline-campaign_MATUMAINI_202305_uni-uni___2024_09_23_17_35_53_515585"
sim.results.uni <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name = "uni",
    summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus", "CMD_Treat_staging", "CMD_Treat"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)
```

## ART distribution

```{r}
#experiment.path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/CROI2025/Baseline-campaign_MATUMAINI_202305_art-art___2024_12_19_14_55_54_577717"
experiment.path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/CROI2025/Baseline-campaign_MATUMAINI_202305_art-art___2024_12_24_17_38_15_018856/"

sim.results.art <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name = "art",
    summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus", "CMD_Treat_staging", "CMD_Treat"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)
```


## Status neutral CMD treatment upon HIV test

```{r}
#experiment.path <- "/gpfs/scratch/citrod01/experiments/MATUMAINI/CROI2025/Baseline-campaign_MATUMAINI_202305_neutral_testing-testing___2024_12_18_17_37_10_681523"
experiment.path <- "/gpfs/scratch/citrod01/experiments/MATUMAINI/CROI2025/Baseline-campaign_MATUMAINI_202305_neutral_testing-testing___2024_12_20_15_52_54_176586"


sim.results.neutral.testing <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name = "neutral.testing",
    summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus", "CMD_Treat_staging", "CMD_Treat"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)
```


## CMD treatment annually for all in HCTTesting Loop

```{r}
#experiment.path <- "/gpfs/scratch/citrod01/experiments/MATUMAINI/CROI2025/Baseline-campaign_MATUMAINI_202305_neutral_annual-annual___2024_12_19_14_52_41_589804"
experiment.path <- "/gpfs/scratch/citrod01/experiments/MATUMAINI/CROI2025/Baseline-campaign_MATUMAINI_202305_neutral_annual-annual___2024_12_25_12_53_07_907145/"


sim.results.neutral.annual <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name = "neutral.annual",
    summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus", "CMD_Treat_staging", "CMD_Treat"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)
```

## Join together

```{r}
sim.results.treatment <- rbind(
  sim.results.neutral.testing, 
  sim.results.neutral.annual, 
  sim.results.baseline, 
  sim.results.art,
  sim.results.uni)

CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results.treatment %>%
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.ix, scenario_name) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>%
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.treatment <- sim.results.treatment %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )
```

## Analyze

### CMD_Treat over time
```{r}
cmdtreat.count <- sim.results.treatment %>% 
  #mutate(Year = ceiling(Year)) %>% 
  filter(Year >= 2020) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(CMD_Treat = sum(CMD_Treat), .groups = 'drop_last') %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(CMD_Treat = mean(CMD_Treat), .groups = 'drop_last')

cmdtreat.count %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = CMD_Treat, color = scenario_name)) + 
  facet_grid(cols = vars(Gender))
            
# sim.results.art %>% 
#   #mutate(Year = ceiling(Year)) %>% 
#   filter(Year >= 2020) %>% 
#   group_by(Year, Gender, scenario_name, sim.ix) %>% 
#   summarize(CMD_Treat = sum(CMD_Treat),
#             CMD_Treat_staging = sum(CMD_Treat_staging), .groups = 'drop_last') %>% 
#   group_by(Year, Gender, scenario_name) %>%  
#   summarize(CMD_Treat = mean(CMD_Treat),
#             CMD_Treat_staging = mean(CMD_Treat_staging), .groups = 'drop_last') %>% 
#   mutate(ratio = CMD_Treat/CMD_Treat_staging) %>% arrange(Gender, Year) %>% 
#   ggplot() + 
#   geom_line(mapping = aes(x = Year, y = ratio, color = scenario_name)) + 
#   facet_grid(cols = vars(Gender))

```
### Ratio of people staged for CMD treatment vs those who receive it

```{r}
cmdtreat.count <- sim.results.treatment %>% 
  #mutate(Year = ceiling(Year)) %>%
  filter(Year >= 2020) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(CMD_Treat = sum(CMD_Treat), CMD_Treat_staging = sum(CMD_Treat_staging), .groups = 'drop_last') %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(CMD_Treat = mean(CMD_Treat), CMD_Treat_staging = mean(CMD_Treat_staging), .groups = 'drop_last') %>% 
  mutate(ratio = case_when(CMD_Treat_staging > 0 ~ CMD_Treat/CMD_Treat_staging, CMD_Treat_staging == 0 ~ 0))

cmdtreat.count %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = ratio, color = scenario_name)) + 
  facet_grid(cols = vars(Gender))
```


## How many people are living with HIV, CMD in 2025?
```{r}
sim.results.neutral %>% 
  filter(Year == 2025, Age >= 15) %>% 
  group_by(Gender, scenario_name, sim.ix) %>% 
  summarize(Infected = sum(Infected * pop.scaling.factor)) %>% 
  group_by(Gender,scenario_name) %>% 
  summarize(Infected = mean(Infected)) %>%
  pivot_wider(id_cols = c("scenario_name"), values_from = c("Infected"), names_from = c("Gender"),
              names_prefix = "Infected_") %>% 
  mutate(Infected = Infected_0 + Infected_1)
```

```{r}
sim.results.neutral %>% 
  filter(Year == 2025, Age >= 15) %>% 
  filter(IP_Key.CMDStatus == "CMD_pos") %>% 
  group_by(Gender, scenario_name, sim.ix) %>% 
  summarize(Population = sum(Population * pop.scaling.factor)) %>% 
  group_by(Gender,scenario_name) %>% 
  summarize(Population = mean(Population)) %>%
  pivot_wider(id_cols = c("scenario_name"), values_from = c("Population"), names_from = c("Gender"),
              names_prefix = "Depressed_") %>% 
  mutate(Depressed = Depressed_0 + Depressed_1)
```

```{r}
sim.results.neutral %>% 
  filter(Year == 2025, Age >= 15) %>% 
  filter(IP_Key.CMDStatus == "CMD_pos") %>% 
  group_by(Gender, scenario_name, sim.ix) %>% 
  summarize(Infected = sum(Infected * pop.scaling.factor)) %>% 
  group_by(Gender,scenario_name) %>% 
  summarize(Infected = mean(Infected)) %>%
  pivot_wider(id_cols = c("scenario_name"), values_from = c("Infected"), names_from = c("Gender"),
              names_prefix = "Infected_") %>% 
  mutate(Infected = Infected_0 + Infected_1)
```

### Impact calculations

```{r}
bt_mean <- function(splits, colname){
  x <- as.data.frame(analysis(splits))
  mean(x[[colname]])
}

# Deaths and Infections
bt_resamples <- bootstraps(hiv.averted.data.scatter %>% filter(scenario_name == "final"), times = 500)

bt_resamples$mean.infected <- map_dbl(bt_resamples$splits, bt_mean, "Newly.Infected_averted")
bt_resamples$mean.infected.pct <- map_dbl(bt_resamples$splits, bt_mean, "Newly.Infected_averted.pct")
bt_resamples$mean.deaths<- map_dbl(bt_resamples$splits, bt_mean, "Died_from_HIV_averted")
bt_resamples$mean.deaths.pct <- map_dbl(bt_resamples$splits, bt_mean, "Died_from_HIV_averted.pct")

infected_95 <- quantile(bt_resamples$mean.infected, probs = c(.025, .975))
deaths_95 <- quantile(bt_resamples$mean.deaths, probs = c(.025, .975))
infected.pct_95 <- quantile(bt_resamples$mean.infected.pct, probs = c(.025, .975))
deaths.pct_95 <- quantile(bt_resamples$mean.deaths.pct, probs = c(.025, .975))

all.stats[all.stats$scenario_name == "final",]$Newly.Infected_averted.lb = infected_95[[1]]
all.stats[all.stats$scenario_name == "final",]$Newly.Infected_averted.ub = infected_95[[2]]
all.stats[all.stats$scenario_name == "final",]$Newly.Infected_averted.pct.lb = infected.pct_95[[1]]
all.stats[all.stats$scenario_name == "final",]$Newly.Infected_averted.pct.ub = infected.pct_95[[2]]

all.stats[all.stats$scenario_name == "final",]$Died_from_HIV_averted.lb = deaths_95[[1]]
all.stats[all.stats$scenario_name == "final",]$Died_from_HIV_averted.ub = deaths_95[[2]]
all.stats[all.stats$scenario_name == "final",]$Died_from_HIV_averted.pct.lb = deaths.pct_95[[1]]
all.stats[all.stats$scenario_name == "final",]$Died_from_HIV_averted.pct.ub = deaths.pct_95[[2]]

bt_resamples <- bootstraps(hiv.averted.data.scatter %>% filter(scenario_name == "neutral"), times = 500)

bt_resamples$mean.infected <- map_dbl(bt_resamples$splits, bt_mean, "Newly.Infected_averted")
bt_resamples$mean.infected.pct <- map_dbl(bt_resamples$splits, bt_mean, "Newly.Infected_averted.pct")
bt_resamples$mean.deaths<- map_dbl(bt_resamples$splits, bt_mean, "Died_from_HIV_averted")
bt_resamples$mean.deaths.pct <- map_dbl(bt_resamples$splits, bt_mean, "Died_from_HIV_averted.pct")

infected_95 <- quantile(bt_resamples$mean.infected, probs = c(.025, .975))
deaths_95 <- quantile(bt_resamples$mean.deaths, probs = c(.025, .975))
infected.pct_95 <- quantile(bt_resamples$mean.infected.pct, probs = c(.025, .975))
deaths.pct_95 <- quantile(bt_resamples$mean.deaths.pct, probs = c(.025, .975))

all.stats[all.stats$scenario_name == "neutral",]$Newly.Infected_averted.lb = infected_95[[1]]
all.stats[all.stats$scenario_name == "neutral",]$Newly.Infected_averted.ub = infected_95[[2]]
all.stats[all.stats$scenario_name == "neutral",]$Newly.Infected_averted.pct.lb = infected.pct_95[[1]]
all.stats[all.stats$scenario_name == "neutral",]$Newly.Infected_averted.pct.ub = infected.pct_95[[2]]

all.stats[all.stats$scenario_name == "neutral",]$Died_from_HIV_averted.lb = deaths_95[[1]]
all.stats[all.stats$scenario_name == "neutral",]$Died_from_HIV_averted.ub = deaths_95[[2]]
all.stats[all.stats$scenario_name == "neutral",]$Died_from_HIV_averted.pct.lb = deaths.pct_95[[1]]
all.stats[all.stats$scenario_name == "neutral",]$Died_from_HIV_averted.pct.ub = deaths.pct_95[[2]]

# cmd
bt_resamples <- bootstraps(cmd.treat.data.scatter %>% filter(scenario_name == "final"), times = 500)
bt_resamples$mean.cmd <- map_dbl(bt_resamples$splits, bt_mean, "CMD_Treat")
cmd_95 <- quantile(bt_resamples$mean.cmd, probs = c(.025, .975))
all.stats[all.stats$scenario_name == "final",]$CMD_Treat.lb = cmd_95[[1]]
all.stats[all.stats$scenario_name == "final",]$CMD_Treat.ub = cmd_95[[2]]

bt_resamples <- bootstraps(cmd.treat.data.scatter %>% filter(scenario_name == "neutral"), times = 500)
bt_resamples$mean.cmd <- map_dbl(bt_resamples$splits, bt_mean, "CMD_Treat")
cmd_95 <- quantile(bt_resamples$mean.cmd, probs = c(.025, .975))
all.stats[all.stats$scenario_name == "neutral",]$CMD_Treat.lb = cmd_95[[1]]
all.stats[all.stats$scenario_name == "neutral",]$CMD_Treat.ub = cmd_95[[2]]

all.stats
```

### Impact of treatment

```{r}
p <- all.stats %>% 
  mutate(scenario_ix = case_match(scenario_name, "baseline" ~ 0, "final" ~ 1, "neutral" ~ 2)) %>% 
  select(scenario_ix,scenario_name, Depression_averted.pct) %>% 
  filter(scenario_name %in% c("uni", "neutral", "art")) %>% 
  pivot_longer(cols = c(Depression_averted.pct), names_to = "metric") %>% 
  ggplot() +
  geom_bar(mapping = aes(x = metric, y = value*100, fill = factor(scenario_name)),
           position=position_dodge2(reverse = TRUE, padding = 0), stat = "identity") + 
  scale_y_continuous(breaks = seq(0,50,10), labels = c("0%", "10%", "20%", "30%", "40%","50%"), expand = expansion(mult = c(0.00,.1))) +
  scale_fill_manual("", values = c("#00671F", "#FF6600", "#0004E7"),
                    breaks = c("baseline", "final", "neutral"), 
                    labels = c("baseline", "final   ", "neutral")) + 
  scale_x_discrete(breaks=c("Depression_averted.pct"),
                   labels=c("Depression Episodes")) + 
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "top")
# + 
#   guides(fill=guide_legend("Depression Treatment Distribution"))

all.stats.plot <- all.stats %>% 
  mutate(scenario_ix = case_match(scenario_name, "baseline" ~ 0, "final" ~ 1, "neutral" ~ 2)) %>% 
  select(scenario_ix,scenario_name, Newly.Infected_averted.pct, Died_from_HIV_averted.pct) %>% 
  filter(scenario_name %in% c("baseline", "final", "neutral")) %>% 
  pivot_longer(cols = c(Newly.Infected_averted.pct, Died_from_HIV_averted.pct), names_to = "metric", values_to = "mean") %>% 
  merge(
    all.stats %>% 
      mutate(scenario_ix = case_match(scenario_name, "baseline" ~ 0, "final" ~ 1, "neutral" ~ 2)) %>% 
      select(scenario_ix,scenario_name, Newly.Infected_averted.pct.lb, Died_from_HIV_averted.pct.lb) %>% 
  filter(scenario_name %in% c("baseline", "final", "neutral")) %>% 
      mutate(Newly.Infected_averted.pct = Newly.Infected_averted.pct.lb,
             Died_from_HIV_averted.pct = Died_from_HIV_averted.pct.lb) %>% 
      select(scenario_ix, scenario_name, Newly.Infected_averted.pct,Died_from_HIV_averted.pct) %>% 
      pivot_longer(cols = c(Newly.Infected_averted.pct, Died_from_HIV_averted.pct), names_to = "metric", values_to =  "lb"),
    by = c("scenario_ix", "scenario_name", "metric")
  ) %>% 
  merge(
    all.stats %>% 
      mutate(scenario_ix = case_match(scenario_name, "baseline" ~ 0, "final" ~ 1, "neutral" ~ 2)) %>% 
      select(scenario_ix,scenario_name, Newly.Infected_averted.pct.ub, Died_from_HIV_averted.pct.ub) %>% 
      filter(scenario_name %in% c("baseline", "final", "neutral")) %>% 
      mutate(Newly.Infected_averted.pct = Newly.Infected_averted.pct.ub,
             Died_from_HIV_averted.pct = Died_from_HIV_averted.pct.ub) %>% 
      select(scenario_ix, scenario_name, Newly.Infected_averted.pct,Died_from_HIV_averted.pct) %>% 
      pivot_longer(cols = c(Newly.Infected_averted.pct, Died_from_HIV_averted.pct), names_to = "metric", values_to =  "ub"),
    by = c("scenario_ix", "scenario_name", "metric")
  ) 


p1 <- all.stats.plot %>% 
  ggplot() +
  geom_bar(mapping = aes(x = metric, y = mean*100, fill = factor(scenario_name)),
           position=position_dodge2(reverse = TRUE, padding = 0), stat = "identity",
           show.legend = TRUE) + 
  geom_errorbar(mapping = aes(x = metric, ymin = lb*100, ymax = ub*100, color = factor(scenario_name)),
                position=position_dodge2(reverse = TRUE, padding = .25), stat = "identity",
                size = 1,# color = "black",
                show.legend = TRUE) + 
  #geom_label(mapping = aes(x = metric, y = value*100, label = metric)) + 
  #geom_text(mapping = aes(x = 1, y = 4.1, label = "HIV Deaths Averted")) + 
  #geom_text(mapping = aes(x = 2, y = 7, label = "HIV Infections Averted")) + 
  scale_y_continuous(
    "% Averted",
    breaks = seq(0,1,.2), 
    labels = c("0%", ".2%", ".4%", ".6%", ".8%",".10%"), 
    expand = expansion(mult = c(0.00,.2))) +
  scale_fill_manual("", values = c("#00671F", "#FF6600", "#0004E7"),
                    breaks = c("baseline", "final", "neutral"), 
                    labels = c("baseline", "final   ", "neutral")) + 
  scale_color_manual("", values = c("black", "black", "black"),
                    breaks = c("baseline", "final", "neutral"), 
                    labels = c("baseline", "final   ", "neutral")) + 
  scale_x_discrete( 
    breaks=c("Newly.Infected_averted.pct", "Died_from_HIV_averted.pct"),
    labels=c("HIV Infections", "HIV Deaths"),
      expand = expansion(mult = c(.6,.6))) +
  #ggtitle("HIV Outcome Improvements\nvs. Depression Treatment Strategy") + 
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"))

p1 
# + 
#   guides(fill=guide_legend("Depression Treatment Distribution"))
```

```{r}
all.stats.plot
```

```{r}
p2 <- all.stats %>% 
  mutate(scenario_id = case_match(scenario_name, "baseline" ~ "", "final" ~ "final", "neutral" ~ "Status Neutral", "art" ~ "ART")) %>% 
  ggplot() +  
  geom_line(all.stats %>% filter(scenario_name != "neutral"),
            mapping = aes(x = CMD_Treat, y = Died_from_HIV_averted)) + 
  geom_point(mapping = aes(x = CMD_Treat, y = Died_from_HIV_averted, color = scenario_name), show.legend = FALSE,
             size = 3) + 
  geom_errorbar(all.stats %>% filter(scenario_name != "baseline"),
                mapping = aes(x = CMD_Treat, ymin = Died_from_HIV_averted.lb, ymax = Died_from_HIV_averted.ub)) + 
  # geom_errorbar(all.stats %>% filter(scenario_name != "baseline"),
  #               mapping = aes(xmin = CMD_Treat.lb, xmax = CMD_Treat.ub,  y = Died_from_HIV_averted)) + 
  #geom_text(mapping = aes(x = CMD_Treat, y = Died_from_HIV_averted, label = scenario_id),
  #          position = position_dodge(width = 1),  vjust =  -0.75) + 
  #ggtitle("HIV Outcome Improvements\nvs. Depression Treatments Administered") + 
  # scale_color_manual("", values = c("black", "#00671F", "#FF6600", "#0004E7"),
  #                 breaks = c("baseline", "uni", "neutral", "art"), 
  #                 labels = c("", "Universal", "Status Neutral   ", "ART")) +
  # scale_y_continuous(
  #   "HIV Infections Averted",
  #   breaks = seq(0,4000,1000), labels = seq(0,4000, 1000), expand = expansion(mult = c(0.01,.1))) +   scale_x_continuous(
  #   "Depression Treatments Administered", breaks = seq(0,4000000, 1000000), labels = c(0, "1M", "2M", "3M", "4M" ),
  #   expand = expansion(mult = c(0.01, .2))
  # ) + 
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"))


p3 <- all.stats %>% 
  mutate(scenario_id = case_match(scenario_name, "baseline" ~ "", "final" ~ "final", "neutral" ~ "Status Neutral", "art" ~ "ART")) %>% 
  ggplot() +  
  geom_line(all.stats %>% filter(scenario_name != "neutral"),
            mapping = aes(x = CMD_Treat, y = Newly.Infected_averted)) + 
  geom_point(mapping = aes(x = CMD_Treat, y = Newly.Infected_averted, color = scenario_name), show.legend = FALSE,
             size = 3) + 
  geom_errorbar(all.stats %>% filter(scenario_name != "baseline"),
                mapping = aes(x = CMD_Treat, ymin = Newly.Infected_averted.lb, ymax = Newly.Infected_averted.ub)) + 
  # geom_text(mapping = aes(x = CMD_Treat, y = Newly.Infected_averted, label = scenario_id),
  #           position = position_dodge(width = 1),  vjust = -0.75) + 
  scale_color_manual("", values = c("black", "#00671F", "#FF6600", "#0004E7"),
                  breaks = c("baseline", "uni", "neutral", "art"), 
                  labels = c("", "Universal", "Status Neutral   ", "ART")) +
  # scale_y_continuous(
  #   "HIV Deaths Averted",
  #   breaks = seq(0,10000,2000), labels = seq(0,10000, 2000), expand = expansion(mult = c(0.01,.1))) + 
  # scale_x_continuous(
  #   "Depression Treatments Administered", breaks = seq(0,4000000, 1000000), labels = c(0, "1M", "2M", "3M", "4M" ),
  #   expand = expansion(mult = c(0.01, .2))
  # ) + 
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans")
        )

p2/p3
```

# Metrics

## What's going on in 2025?

### PLHIV 

```{r}
plhiv.2025 <- sim.results.treatment %>% 
  filter(Year == 2025, Age >= 15) %>% 
  group_by(Gender, scenario_name, sim.ix) %>% 
  summarize(Infected = sum(Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Gender,scenario_name) %>% 
  summarize(Infected = mean(Infected), .groups = "keep") %>%
  pivot_wider(id_cols = c("scenario_name"), values_from = c("Infected"), names_from = c("Gender"),
              names_prefix = "Infected_") %>% 
  select(scenario_name, Infected_Male = Infected_0, Infected_Female = Infected_1) %>% 
  mutate(Infected = Infected_Male + Infected_Female)

plhiv.2025
```

### People living with depression

```{r}
pldep.2025 <- sim.results.treatment %>% 
  filter(Year == 2025, Age >=15) %>%
  filter(IP_Key.CMDStatus == "CMD_pos") %>%
  group_by(scenario_name, sim.ix) %>% 
  summarize(Population = sum(Population * pop.scaling.factor), .groups = "drop_last" ) %>% 
  group_by(scenario_name) %>% 
  summarize(Depression = mean(Population), .groups = "drop_last")

pldep.2025
```

### People with HIV living with depression

```{r}
plhiv.dep.2025 <-  sim.results.treatment %>% 
  filter(Year == 2025, Age >= 15) %>% 
  group_by(scenario_name, IP_Key.CMDStatus, sim.ix) %>% 
  summarize(Population = sum(Population * pop.scaling.factor),
            Infected = sum(Infected * pop.scaling.factor),
            .groups = 'drop_last') %>% 
  group_by(scenario_name, IP_Key.CMDStatus) %>% 
  summarize(Population = mean(Population),
            PLHIV = mean(Infected), .groups = 'drop_last') %>% 
  pivot_wider(
    id_cols = scenario_name,
    values_from = c("Population", "PLHIV"), 
    names_from = IP_Key.CMDStatus)

plhiv.dep.2025
```

## HIV prevalence over time

```{r}
prev.time.data <- sim.results.treatment %>%
  EMODAnalyzeR::calculate.prevalence(
    stratify_columns = c("Year", "Gender", "sim.ix", "scenario_name")
  ) %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(Infected = mean(Infected),
            Population = mean(Population),
            Prevalence = mean(Prevalence), .groups = 'drop_last') %>%
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- ggplot() +
      geom_line(data= prev.time.data %>% filter(Year > 1985),
              aes(x=Year, y=Prevalence, group=scenario_name, color=scenario_name), linewidth=.5) +
    facet_wrap(~ Gender, ncol=2) +
    #xlab("Year")+
    #xlim(c(date.start, date.end)) +
    #ylab("Prevalence") +
    theme_bw(base_size=16) +
    guides(color = guide_legend(ncol = 2, byrow = TRUE, keywidth = 2, keyheight = 1)) +
    theme(legend.position="top", legend.text=element_text(size=10)) +
    scale_x_continuous(breaks = seq(1985,2050,10)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    #ylab("HIV Prevalence (%)") +
    scale_color_manual(values=c("blue","red","darkgreen","orange","black","purple", "pink"))
p

p + xlim(2025,2035)
```

## PLHIV over time

```{r}
plhiv.time.data <- sim.results.treatment %>% 
  filter(Age >= 15) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(PLHIV = sum(Infected * pop.scaling.factor), .groups = 'drop_last') %>% 
  group_by(Year, Gender,scenario_name) %>% 
  summarize(PLHIV = mean(PLHIV), .groups = 'drop_last') %>%
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- ggplot() +
    geom_line(data= plhiv.time.data %>% filter(Year > 1985),
              aes(x=Year, y=PLHIV, group=scenario_name, color=scenario_name), linewidth=.5) +
    facet_wrap(~ Gender, ncol=2, scales = "free_y") +
    theme_bw(base_size=16) +
    guides(color = guide_legend(ncol = 2, byrow = TRUE, keywidth = 2, keyheight = 1)) +
    theme(legend.position="top", legend.text=element_text(size=10)) +
    scale_x_continuous(breaks = seq(1985,2050,10)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    #ylab("HIV Prevalence (%)") +
    scale_color_manual(values=c("blue","red","darkgreen","orange","black","purple", "pink"))

p
```

```{r}
p <- ggplot() +
    geom_line(data= plhiv.time.data %>% filter(Year > 2020),
              aes(x=Year, y=PLHIV, group=scenario_name, color=scenario_name), linewidth=.5) +
    facet_wrap(~ Gender, ncol=2, scales = "free_y") +
    theme_bw(base_size=16) +
    guides(color = guide_legend(ncol = 2, byrow = TRUE, keywidth = 2, keyheight = 1)) +
    theme(legend.position="top", legend.text=element_text(size=10)) +
    scale_x_continuous(breaks = seq(2020,2035,2)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    #ylab("HIV Prevalence (%)") +
    scale_color_manual(values=c("blue","red","darkgreen","orange","black","purple", "pink"))

p
```

## HIV new infections over time

```{r}
hiv.averted.data <- sim.results.treatment %>% 
  filter(Age >=15) %>%
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV * pop.scaling.factor),
            Newly.Infected = sum(Newly.Infected * pop.scaling.factor), .groups = 'drop_last') %>% 
  group_by(Year, Gender, scenario_name) %>%
  summarize(Died_from_HIV = mean(Died_from_HIV),
            Newly.Infected = mean(Newly.Infected), .groups = 'drop_last') %>%
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- ggplot() +
    geom_line(data= hiv.averted.data %>% filter(Year > 1985),
              aes(x=Year, y=Newly.Infected, group=scenario_name, color=scenario_name), linewidth=.5) +
    facet_wrap(~ Gender, ncol=2, scales = "free_y") +
    theme_bw(base_size=16) +
    guides(color = guide_legend(ncol = 2, byrow = TRUE, keywidth = 2, keyheight = 1)) +
    theme(legend.position="top", legend.text=element_text(size=10)) +
    scale_x_continuous(breaks = seq(1985,2050,10)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    #ylab("HIV Prevalence (%)") +
    scale_color_manual(values=c("blue","red","darkgreen","orange","black","purple", "pink"))

p
```
```{r}
p <- ggplot() +
    geom_line(data= hiv.averted.data %>% filter(Year > 2020),
              aes(x=Year, y=Newly.Infected, group=scenario_name, color=scenario_name), linewidth=.5) +
    facet_wrap(~ Gender, ncol=2, scales = "free_y") +
    theme_bw(base_size=16) +
    guides(color = guide_legend(ncol = 2, byrow = TRUE, keywidth = 2, keyheight = 1)) +
    theme(legend.position="top", legend.text=element_text(size=10)) +
    scale_x_continuous(breaks = seq(2020,2035,2)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    #ylab("HIV Prevalence (%)") +
    scale_color_manual(values=c("blue","red","darkgreen","orange","black","purple", "pink"))

p
```


## HIV deaths over time

```{r}
p <- ggplot() +
    geom_line(data= hiv.averted.data %>% filter(Year > 1985),
              aes(x=Year, y=Died_from_HIV, group=scenario_name, color=scenario_name), linewidth=.5) +
    facet_wrap(~ Gender, ncol=2, scales = "free_y") +
    theme_bw(base_size=16) +
    guides(color = guide_legend(ncol = 2, byrow = TRUE, keywidth = 2, keyheight = 1)) +
    theme(legend.position="top", legend.text=element_text(size=10)) +
    scale_x_continuous(breaks = seq(1985,2035,5)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    #ylab("HIV Prevalence (%)") +
    scale_color_manual(values=c("blue","red","darkgreen","orange","black","purple", "pink"))

p
```


```{r}
p <- ggplot() +
    geom_line(data= hiv.averted.data %>% filter(Year > 2020),
              aes(x=Year, y=Died_from_HIV, group=scenario_name, color=scenario_name), linewidth=.5) +
    facet_wrap(~ Gender, ncol=2, scales = "free_y") +
    theme_bw(base_size=16) +
    guides(color = guide_legend(ncol = 2, byrow = TRUE, keywidth = 2, keyheight = 1)) +
    theme(legend.position="top", legend.text=element_text(size=10)) +
    scale_x_continuous(breaks = seq(2020,2035,2)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    #ylab("HIV Prevalence (%)") +
    scale_color_manual(values=c("blue","red","darkgreen","orange","black","purple", "pink"))

p
```


## HIV infections and deaths averted

```{r}
hiv.averted.data.agg <- hiv.averted.data %>% 
  filter(Year >= 2025) %>% 
  group_by(Gender, scenario_name) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV * pop), 
            Newly.Infected = sum(Newly.Infected), .groups = 'drop_last')

hiv.averted.data.agg <- hiv.averted.data.agg %>% 
  merge(
    hiv.averted.data.agg %>% 
      filter(scenario_name == 'baseline') %>% 
      select(Gender, Died_from_HIV.baseline = Died_from_HIV, Newly.Infected.baseline = Newly.Infected), 
    by = c("Gender")
  ) %>% 
  mutate(
    Died_from_HIV.averted = Died_from_HIV.baseline - Died_from_HIV,
    Newly.Infected.averted = Newly.Infected.baseline - Newly.Infected,
    )

hiv.averted.data.agg %>% 
  group_by(scenario_name) %>% 
  summarize(Died_from_HIV.averted = sum(Died_from_HIV.averted),
            Newly.Infected.averted = sum(Newly.Infected.averted), .groups = 'drop_last')
```
### Generate CIs for infections and deaths averted

```{r}
hiv.averted.stats <- sim.results.treatment %>% 
  filter(Age >=15, Year >= 2025) %>%
  group_by(scenario_name, sim.ix) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV * pop.scaling.factor),
            Newly.Infected = sum(Newly.Infected * pop.scaling.factor), .groups = 'drop_last') %>% 
  ungroup()

hiv.averted.stats <- hiv.averted.stats %>% 
  merge(
    hiv.averted.stats %>% 
      filter(scenario_name == 'baseline') %>% 
      select(sim.ix, Died_from_HIV.baseline = Died_from_HIV, Newly.Infected.baseline = Newly.Infected), 
    by = c("sim.ix")
  ) %>% 
  mutate(
    Died_from_HIV.averted = Died_from_HIV.baseline - Died_from_HIV,
    Newly.Infected.averted = Newly.Infected.baseline - Newly.Infected,
    ) %>% 
  mutate(
    Died_from_HIV.averted.pct = Died_from_HIV.averted/Died_from_HIV.baseline,
    Newly.Infected.averted.pct = Newly.Infected.averted/Newly.Infected.baseline
  )


bt_mean <- function(splits, colname){
  x <- as.data.frame(analysis(splits))
  mean(x[[colname]])
}

bt_resamples <- bootstraps(hiv.averted.stats %>% filter(scenario_name == 'art'), times = 500)

bt_resamples$mean.metric <- map_dbl(bt_resamples$splits, bt_mean, "Died_from_HIV.averted")

mean(bt_resamples$mean.metric)

calculate.CI.by.metric = function(data, scenario.name, metric, n = 500){
  bt_resamples <- bootstraps(data %>% filter(scenario_name == scenario.name), times = n)
  
  bt_resamples$mean.metric <- map_dbl(bt_resamples$splits, bt_mean, metric)
  metric_95 <- quantile(bt_resamples$mean.metric, probs = c(0.025, 0.975))
  
  return(
      data.frame(
      scenario_name = scenario.name, 
      metric = metric,
      metric.mean = mean(bt_resamples$mean.metric),
      metric.lb = metric_95[[1]], 
      metric.ub = metric_95[[2]]
    )
  )
}

metric.names = c(
  "Died_from_HIV.averted",
  "Died_from_HIV.averted.pct",
  "Newly.Infected.averted",
  "Newly.Infected.averted.pct"
)

scenario_names = hiv.averted.stats$scenario_name %>% unique 

metrics = data.frame()

for (i in metric.names){
  for (j in scenario_names) {
    
    #print(c(i,j))
    h <- calculate.CI.by.metric(
      data = hiv.averted.stats, 
      scenario.name = j,
      metric = i)
    
    metrics = rbind(metrics, h)
  }
}

metrics
```



## Depression prevalence over time

```{r}
cmd.prev.time.data <- sim.results.treatment %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >= 15) %>% 
  group_by(Year, Gender, scenario_name, IP_Key.CMDStatus, sim.ix) %>% 
  summarize(Population = sum(Population* pop.scaling.factor), .groups = 'drop_last') %>% 
  pivot_wider(
    id_cols = c(Year, Gender, scenario_name, sim.ix) , 
    values_from = c(Population), 
    names_from = c(IP_Key.CMDStatus)
  ) %>% 
  mutate(Population = CMD_neg + CMD_pos + CMD_recovered + CMD_treated) %>% 
  mutate(CMD.prev = CMD_pos/Population) %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(
    CMD.prev = mean(CMD.prev), 
    Population = mean(Population), 
    CMD_neg = mean(CMD_neg), 
    CMD_pos = mean(CMD_pos), 
    CMD_recovered = mean(CMD_recovered), 
    CMD_treated = mean(CMD_treated), 
    .groups = 'drop_last') %>%
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- ggplot() + 
    geom_line(data= cmd.prev.time.data %>% filter(Year > 1985),
              aes(x=Year, y=CMD.prev, group=scenario_name, color=scenario_name), linewidth=.5) +
    facet_wrap(~ Gender, ncol=2) +
    theme_bw(base_size=16) +
    guides(color = guide_legend(ncol = 2, byrow = TRUE, keywidth = 2, keyheight = 1)) +
    theme(legend.position="top", legend.text=element_text(size=10)) +
    scale_x_continuous(breaks = seq(1985,2050,10)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    #ylab("HIV Prevalence (%)") +
    scale_color_manual(values=c("blue","red","darkgreen","orange","black","purple", "pink"))

p
```

## Depression episodes over time

```{r}
p <- ggplot() + 
    geom_line(data= cmd.prev.time.data %>% filter(Year > 1985),
              aes(x=Year, y=CMD_pos, group=scenario_name, color=scenario_name), linewidth=.5) +
    facet_wrap(~ Gender, ncol=2) +
    theme_bw(base_size=16) +
    guides(color = guide_legend(ncol = 2, byrow = TRUE, keywidth = 2, keyheight = 1)) +
    theme(legend.position="top", legend.text=element_text(size=10)) +
    scale_x_continuous(breaks = seq(1985,2050,10)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    #ylab("HIV Prevalence (%)") +
    scale_color_manual(values=c("blue","red","darkgreen","orange","black","purple", "pink"))

p
```
## Depression episodes averted

## HIV-related DALYs

### HIV-related DALYs averted

## Depression-related DALYs

### Depression-related DALYs averted