---
title: "treatment_effects.Rmd"
output: html_document
---


```{r Load Libraries}
library(tidyverse)
library(tidyr)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
library(readxl)
devtools::install_github("BershteynLab/EMODAnalyzeR")
```

```{r}
CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385
```


```{r}
# Confidence interval functions
lower_ci <- function(mean, se, n, conf_level = 0.95){
  lower_ci <- mean - qt(1 - ((1 - conf_level) / 2), n - 1) * se
  return(lower_ci)
}
upper_ci <- function(mean, se, n, conf_level = 0.95){
  upper_ci <- mean + qt(1 - ((1 - conf_level) / 2), n - 1) * se
  return(upper_ci)
}
```


# HIV-Depression model postprocessing

The "minimal scenario" set of HIV-CMD interactions
1. Depression dynamics
  1. Age/sex-specific annual incidence of depression
  2. HIV+ status also increases depression incidence
  3. Relapse rate equal to incidence rate
2. Depression-caused increase to incidence - CoitalActRiskFactor increases from 1 to 1.646
3. Depression-caused delays to diagnosis (2/3 of depressed skip diagnosis)
4. Depression-caused dropout from ART (mean time 5 years for depressed, 10 years for non-depressed)
5. Depression-caused non-adherence to ART

We are going to compare the minimal scenario against a number of scenarios where treatment is implemented:

1. "Baseline" - minimal scenario, as described above
2. Universal test and Treat - `uni.tt`- all individuals receive treatment
  * Diagnosis is 100% specific and sensitive
  * 100% of patients have an effective treatment response
  * Treatment response consists of shortening symptoms, delaying recurrence/relapse
3. Targeted depression treatment for PLHIV - `screen.tt`
  * PLHIV can receive depression treatment upon first HIV diagnosis
  * PLHIV can receive depression treatment as part of routine HIV 
  * Again, diagnosis is 100% specific and sensitive, and 100% of patients have a positive response
  
These results were presented at the 2023 Global Mental Health Research without Borders conference, and again at Epidemics.
a
# Read in the data

## Minimal scenario

```{r}
sim.results.minimal <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/treatment/Baseline-campaign_MATUMAINI_202305-baseline/ReportHIVByAgeAndGender/",
  scenario_name = 'baseline',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed", 
                        "CMD_Treat","CMD_HIV_screening","CMD_Treat_diagnosis"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

sim.results.pop.scaling <- sim.results.minimal %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.minimal <- sim.results.minimal %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )
```

## Universal Test and Treat

```{r}
sim.results.uni.tt <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/treatment/Baseline-campaign_MATUMAINI_202305-treat_uni/ReportHIVByAgeAndGender/",
  scenario_name = 'uni.tt',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed", 
                        "CMD_Treat","CMD_HIV_screening","CMD_Treat_diagnosis"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

sim.results.pop.scaling <- sim.results.uni.tt %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.uni.tt <- sim.results.uni.tt %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```


## Screening upon HIV diagnosis

```{r}
 # sim.results.screen.tt <- EMODAnalyzeR::read.simulation.results(
 #  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/treatment/Baseline-campaign_MATUMAINI_202305_screening-treat_screen/ReportHIVByAgeAndGender/",
  
sim.results.screen.tt <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_screening-treat_screen___2023_10_26_00_29_29_944124/",
  scenario_name = 'screen.tt',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed", 
                        "CMD_Treat","CMD_HIV_screening","CMD_Treat_diagnosis"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

sim.results.pop.scaling <- sim.results.screen.tt %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.screen.tt <- sim.results.screen.tt %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

This is a bit of a weird one, I accidentally made it so that both art and non art people would receive treatment
But, it should be the same as baseline, so let's see if it works at all:
```{r}
 # sim.results.screen.tt <- EMODAnalyzeR::read.simulation.results(
 #  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_MATUMAINI_MalariaOngoing/treatment/Baseline-campaign_MATUMAINI_202305_screening-treat_screen/ReportHIVByAgeAndGender/",
  
sim.results.screen.tt.1 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  # accidentally made it so art and non art people would receive treatment
  #experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_screening-treat_screen___2023_10_26_23_05_16_751507",
  # only 60 of these cleared :( 
  # experiment_path ="/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_screening-treat_screen___2023_10_27_08_20_43_004256",
  experiment_path = "/gpfs/scratch/citrod01/experiments/MATUMAINI/Baseline-campaign_MATUMAINI_202305_screening-treat_screen___2023_10_27_11_40_20_080236",
  scenario_name = 'screen.tt',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed", 
                        "CMD_Treat","CMD_HIV_screening","CMD_Treat_diagnosis"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.CMDStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

sim.results.pop.scaling <- sim.results.screen.tt.1 %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results.screen.tt.1 <- sim.results.screen.tt.1 %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )
```



## Combine datasets

```{r}
sim.results.all <- rbind(sim.results.minimal, sim.results.uni.tt, sim.results.screen.tt.1)# sim.results.screen.tt)
```

# Plots

## HIV Prevalence

```{r}
ingest.file.base = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_Baseline_MalariaOngoing_original/Data/calibration_ingest_form_Nyanza.xlsm"

obs.prev.sheet.base <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-Prevalence")
```

### HIV prevalence, all scenarios
```{r, fig.width=8}
data <- EMODAnalyzeR::calculate.prevalence(
  sim.results.all %>% filter(Age <= 50, Age >=15),
         stratify_columns = c("Year", "Gender", "sim.id", "scenario_name"),
         numerator = "Infected",
         denominator = "Population")

prev.data.mean <- data %>% filter(Year >= 2004) %>% 
  group_by(Year, Gender, scenario_name) %>%
  summarize(sum(Infected))

prev.data.mean <- prev.data.mean %>%
    dplyr::group_by(Year, Gender, scenario_name) %>%
    dplyr::summarise(Prevalence = mean(Prevalence), .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

ggplot() +
    geom_line(data= prev.data.mean %>% filter(Year > 2000),
              aes(x=Year, y=Prevalence, group=scenario_name, color=scenario_name), linewidth=.75) +
    facet_wrap(~ Gender, ncol=2) +
    xlab("Year")+
    #xlim(c(date.start, date.end)) +
    ylab("Prevalence") +
    theme_bw(base_size=16) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    scale_x_continuous(breaks = seq(1980,2040,10)) +
    theme(legend.position="bottom") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(strip.background = element_rect(colour="black", fill="white")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
      ylab("HIV Prevalence (%)") + 
    scale_color_manual(values=c("blue","red","darkgreen","orange")) +
    geom_point(data = obs.prev.sheet.base %>%
                 filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
               mapping = aes(x = Year, y = Prevalence)) + 
    geom_errorbar(data = obs.prev.sheet.base %>%
               filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
               mapping = aes(x = Year, ymin = lb, ymax = ub))

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treat_HIV_prev.pdf",
#        width = 8, height = 6, units = "in")
```


### Change in prevalence from 2020-2040
```{r}
data <- EMODAnalyzeR::calculate.prevalence(
  sim.results.all %>% filter(Age <= 50, Age >=15),
         stratify_columns = c("Year", "sim.id", "scenario_name"),
         numerator = "Infected",
         denominator = "Population")

prev.data.mean <- data %>%
    dplyr::group_by(Year, scenario_name) %>%
    dplyr::summarise(Prevalence = mean(Prevalence), .groups = 'keep')

prev.data.mean %>% filter(Year %in% c(2020, 2040))
```


### HIV prevalence calibration plot
```{r, fig.height=6, fig.width =8}

ggplot() +
      geom_line(data= prev.data.mean %>% filter(Year > 2000, scenario_name == "baseline"),
              aes(x=Year, y=Prevalence, group=scenario_name, color=scenario_name), linewidth=2,  show.legend = FALSE) +
    facet_wrap(~ Gender, ncol=2) +
    xlab("Year")+
    #xlim(c(date.start, date.end)) +
    ylab("Prevalence") +
    theme_bw(base_size=16) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    scale_x_continuous(breaks = seq(1980,2040,10)) +
    theme(legend.position="bottom") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(strip.background = element_rect(colour="black", fill="white")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
      ylab("HIV Prevalence (%)") + 
    scale_color_manual(values=c("blue","red","darkgreen","orange")) +
    geom_point(data = obs.prev.sheet.base %>%
                 filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
               mapping = aes(x = Year, y = Prevalence) , color = 'black', size = 3, shape = 15) + 
    geom_errorbar(data = obs.prev.sheet.base %>%
               filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
               mapping = aes(x = Year, ymin = lb, ymax = ub), color = 'black', size = 1)

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treat_HIV_calib.pdf",
#        width = 10, height = 5, units = "in")
```


## Depression

### Depression prevalence by HIV status

```{r, fig.width=8, fig.height=8}
data.cmd <- sim.results.all %>% filter(Age > 18) %>% 
  mutate(HIVneg = Population - Infected) %>% 
  mutate(Year = ceiling(Year)) %>% 
  group_by(Year, Gender, sim.id, IP_Key.CMDStatus, scenario_name) %>% 
  summarize(Population = sum(Population),
            HIVneg = sum(HIVneg),
            Infected = sum(Infected), .groups = 'keep') %>% 
  ungroup() %>% 
  pivot_wider(id_cols = c(Year, Gender, sim.id, scenario_name),
              names_from = c(IP_Key.CMDStatus),
              values_from = c(Population, HIVneg, Infected))  %>% 
  mutate(Population_total = Population_CMD_pos + Population_CMD_neg + Population_CMD_recovered + Population_CMD_treated,
         HIVneg_total = HIVneg_CMD_pos + HIVneg_CMD_neg + HIVneg_CMD_recovered + HIVneg_CMD_treated,
         Infected_total = Infected_CMD_pos + Infected_CMD_neg + Infected_CMD_recovered + Infected_CMD_treated) %>% 
  mutate(CMD_prev_overall = case_when(Population_total == 0 ~ 0,
                                    Population_total > 0 ~ Population_CMD_pos/Population_total),
         CMD_prev_HIVneg = case_when(HIVneg_total == 0 ~ 0,
                                    HIVneg_total > 0 ~ HIVneg_CMD_pos/HIVneg_total),
         CMD_prev_Infected = case_when(Infected_total == 0 ~ 0,
                                    Infected_total > 0 ~ Infected_CMD_pos/Infected_total)) %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

data.cmd.mean <- data.cmd %>% 
  group_by(Year, Gender, scenario_name) %>%
  summarize(Overall = mean(CMD_prev_overall), Overall_sd = sd(CMD_prev_overall),
            HIVneg = mean(CMD_prev_HIVneg), HIVneg_sd = sd(CMD_prev_HIVneg),
            Infected = mean(CMD_prev_Infected), Infected_sd = sd(CMD_prev_Infected),
            .groups = "keep") %>% 
  ungroup()

# Plot  
p = ggplot() +
  geom_line( data = data.cmd.mean %>% 
                    select(Year, Gender, Overall, Infected, HIVneg, scenario_name) %>% 
                    pivot_longer(cols = c(Overall, Infected, HIVneg),
                                 names_to = "Depression.Prevalence", 
                                 values_to = "CMD_prev"),
    mapping = aes(x = Year, y = CMD_prev, color = Depression.Prevalence), 
    size = 1.0) + 
  scale_y_continuous(limits = c(0.0,.22)) + 
  scale_color_manual(values=c("darkgreen","orange", "black")) +
  facet_wrap(scenario_name ~ Gender, ncol=2) +
  xlab("Year")+ylab("") + 
  ggtitle("Depression Prevalence by HIV status") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(1980,2040,10)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_depression_prev.pdf",
#       width = 8, height = 6, units = "in")
```

### Depression prevalence figures
For building out the figure across multiple slides

```{r, fig.width=10, fig.height=5}
p = ggplot() +
  geom_line( data = data.cmd.mean %>% 
                    select(Year, Gender, Overall, Infected, HIVneg, scenario_name) %>% 
                    pivot_longer(cols = c(Overall, Infected, HIVneg),
                                 names_to = "Depression.Prevalence", 
                                 values_to = "CMD_prev") %>% 
               filter(Depression.Prevalence %in% c("Overall", "Infected")) %>% 
               filter(Year > 2000) %>% 
               mutate(scenario.id = case_when(scenario_name == "baseline" ~ "1",
                                scenario_name == "uni.tt" ~ "2",
                                scenario_name == "screen.tt" ~ "3")) %>%
                filter(scenario_name == "baseline"),
    mapping = aes(x = Year, y = CMD_prev, color = scenario.id), 
    linewidth=2,  
    show.legend = FALSE) + 
  scale_y_continuous(limits = c(0.0,.22)) + 
  scale_color_manual(values=c("#1600FF", "#9c9c9c","#AD130B")) +
  facet_grid(cols = vars(Gender), rows = vars(Depression.Prevalence)) + 
  xlab("Year")+ylab("") + 
  #ggtitle("Depression Prevalence by HIV status") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(1980,2040,10)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_depression_prev_1.pdf",
      width = 10, height = 5, units = "in")
```

```{r, fig.width=10, fig.height=5}
p = ggplot() +
  geom_line( data = data.cmd.mean %>% 
                    select(Year, Gender, Overall, Infected, HIVneg, scenario_name) %>% 
                    pivot_longer(cols = c(Overall, Infected, HIVneg),
                                 names_to = "Depression.Prevalence", 
                                 values_to = "CMD_prev") %>% 
               filter(Depression.Prevalence %in% c("Overall", "Infected")) %>% 
               filter(Year > 2000) %>% 
               mutate(scenario.id = case_when(scenario_name == "baseline" ~ "1",
                                scenario_name == "uni.tt" ~ "2",
                                scenario_name == "screen.tt" ~ "3")) %>%
                filter(scenario_name %in% c("baseline", 'uni.tt')),
    mapping = aes(x = Year, y = CMD_prev, color = scenario.id), 
    linewidth=2,  
    show.legend = FALSE) + 
  scale_y_continuous(limits = c(0.0,.22)) + 
  scale_color_manual(values=c("#1600FF", "#9c9c9c","#AD130B")) +
  facet_grid(cols = vars(Gender), rows = vars(Depression.Prevalence)) + 
  xlab("Year")+ylab("") + 
  #ggtitle("Depression Prevalence by HIV status") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(1980,2040,10)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_depression_prev_2.pdf",
      width = 10, height = 5, units = "in")
```

```{r, fig.width=10, fig.height=5}
p = ggplot() +
  geom_line( data = data.cmd.mean %>% 
                    select(Year, Gender, Overall, Infected, HIVneg, scenario_name) %>% 
                    pivot_longer(cols = c(Overall, Infected, HIVneg),
                                 names_to = "Depression.Prevalence", 
                                 values_to = "CMD_prev") %>% 
               filter(Depression.Prevalence %in% c("Overall", "Infected")) %>% 
               filter(Year > 2000) %>% 
               mutate(scenario.id = case_when(scenario_name == "baseline" ~ "1",
                                scenario_name == "uni.tt" ~ "2",
                                scenario_name == "screen.tt" ~ "3")),
    mapping = aes(x = Year, y = CMD_prev, color = scenario.id), 
    linewidth=2,  
    show.legend = FALSE) + 
  scale_y_continuous(limits = c(0.0,.22)) + 
  scale_color_manual(values=c("#1600FF", "#9c9c9c","#AD130B")) +
  facet_grid(cols = vars(Gender), rows = vars(Depression.Prevalence)) + 
  xlab("Year")+ylab("") + 
  #ggtitle("Depression Prevalence by HIV status") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(1980,2040,10)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_depression_prev_3.pdf",
      width = 10, height = 5, units = "in")
```

### Depression Treatment 


```{r, fig.height=8, fig.width=6}
data.cmd <- sim.results.all %>% filter(Age > 18) %>% 
  mutate(HIVneg = Population - Infected) %>% 
  mutate(Year = ceiling(Year)) %>% 
  group_by(Year, Gender, sim.id, IP_Key.CMDStatus, scenario_name) %>% 
  summarize(Population = sum(Population),
            HIVneg = sum(HIVneg),
            Infected = sum(Infected), .groups = 'keep') %>% 
  ungroup() %>% 
  pivot_wider(id_cols = c(Year, Gender, sim.id, scenario_name),
              names_from = c(IP_Key.CMDStatus),
              values_from = c(Population, HIVneg, Infected))  %>% 
  mutate(Population_total = Population_CMD_pos + Population_CMD_neg + Population_CMD_recovered + Population_CMD_treated,
         HIVneg_total = HIVneg_CMD_pos + HIVneg_CMD_neg + HIVneg_CMD_recovered + HIVneg_CMD_treated,
         Infected_total = Infected_CMD_pos + Infected_CMD_neg + Infected_CMD_recovered + Infected_CMD_treated) %>% 
  mutate(CMD_prev_overall = case_when(Population_total == 0 ~ 0,
                                    Population_total > 0 ~ Population_CMD_pos/Population_total),
         CMD_prev_HIVneg = case_when(HIVneg_total == 0 ~ 0,
                                    HIVneg_total > 0 ~ HIVneg_CMD_pos/HIVneg_total),
         CMD_prev_Infected = case_when(Infected_total == 0 ~ 0,
                                    Infected_total > 0 ~ Infected_CMD_pos/Infected_total),
         CMD_treat_overall = case_when(Population_total == 0 ~ 0,
                                    Population_total > 0 ~ Population_CMD_treated/Population_total),
         CMD_treat_HIVneg = case_when(HIVneg_total == 0 ~ 0,
                                    HIVneg_total > 0 ~ HIVneg_CMD_treated/HIVneg_total),
         CMD_treat_Infected = case_when(Infected_total == 0 ~ 0,
                                    Infected_total > 0 ~ Infected_CMD_treated/Infected_total)) %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

data.cmd.mean <- data.cmd %>% 
  group_by(Year, Gender, scenario_name) %>%
  summarize(Overall = mean(CMD_prev_overall), Overall_sd = sd(CMD_prev_overall),
            HIVneg = mean(CMD_prev_HIVneg), HIVneg_sd = sd(CMD_prev_HIVneg),
            Infected = mean(CMD_prev_Infected), Infected_sd = sd(CMD_prev_Infected),
            treat.overall = mean(CMD_treat_overall),
            treat.HIVneg = mean(CMD_treat_HIVneg),
            treat.HIVpos = mean(CMD_treat_Infected),
            .groups = "keep") %>% 
  ungroup()

data.cmd.mean %>% 
  ggplot() + 
  geom_line( data = data.cmd.mean %>% 
                    select(Year, Gender, treat.overall, treat.HIVpos, treat.HIVneg, scenario_name) %>% 
                    pivot_longer(cols = c(treat.overall, treat.HIVneg, treat.HIVpos),
                                 names_to = "Treatment.Prevalence", 
                                 values_to = "treat_prev") %>% 
               #filter(Depression.Prevalence %in% c("Overall", "Infected")) %>% 
               filter(Year > 2000) %>% 
               mutate(scenario.id = case_when(scenario_name == "baseline" ~ "1",
                                scenario_name == "uni.tt" ~ "2",
                                scenario_name == "screen.tt" ~ "3")),
    mapping = aes(x = Year, y = treat_prev, color = scenario.id), 
    linewidth=2,  
    show.legend = TRUE) + 
 # scale_y_continuous(limits = c(0.0,.22)) + 
  scale_color_manual(values=c("#1600FF", "#9c9c9c","#AD130B")) +
  facet_grid(cols = vars(Gender), rows = vars(Treatment.Prevalence)) + 
  xlab("Year")+ylab("") + 
  #ggtitle("Depression Prevalence by HIV status") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(1980,2040,10)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```


How many treatment events are there?
```{r}
data.cmd %>% ggplot() + 
geom_line(mapping = aes(x = Year, y = Population_CMD_treated, color = scenario_name))
data.cmd %>% filter(scenario_name == "screen.tt") %>% group_by(Year) %>% summarize(sum(Population_CMD_treated))
```




### Number of depression episodes

```{r, fig.width=8in}
data <- sim.results.all %>% 
  #mutate(Year = ceiling(Year)) %>% 
  filter(Year >= 1985,
         IP_Key.CMDStatus == "CMD_pos") %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(deps = sum(Population * pop.scaling.factor), 
            .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p = ggplot() +
  geom_line( data,
    mapping = aes(x = Year, y = deps, color = scenario_name), 
    size = 1.0) + 
  #scale_y_continuous(limits = c(0.05,.22)) + 
  facet_wrap( ~ Gender, ncol=2) +
  scale_color_manual(values=c("blue","red","darkgreen","orange")) +
  xlab("Year")+ylab("") + 
  ggtitle("Number of depressive episodes") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(1980,2040,10)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_depression_episodes.pdf",
#       width = 8, height = 6, units = "in")
```

### Depression calibration

```{r}
obs.cmdprev.sheet <- data.frame(Year = 2004, 
           Gender = c("Male", "Male", "Male", "Male", "Male", "Male", "Male", 
                    "Female", "Female", "Female", "Female", "Female", "Female", "Female"),
           AgeBin =  c("[18:24)", "[25:29)", "[30:39)", "[40:44)", "[45:49)", "[50:59)", "[60:99)",
                      "[18:24)", "[25:29)", "[30:39)", "[40:44)", "[45:49)", "[50:59)", "[60:99)"),
           CMDPrevalence = c(0.03, 0.069, 0.098, 0.087, 0.11, 0.13, 0.2, 
                             0.065, 0.086, 0.067, 0.12, 0.13, 0.079, 0.051),
           CMDPrevalence.lb = c(0, 0, 0,0.013,0.045,0.034,0.13,0.024,0.041,0.026,0.058,0.037,0.03,0.0043),
           CMDPrevalence.ub = c(0.069,0.14,0.2,0.16,0.18,0.22,0.27,0.11,0.13,0.11,0.17,0.22,0.12,0.099)
)
obs.cmdprev.sheet$AgeBin_index = factor(obs.cmdprev.sheet$AgeBin,labels = 1:7)
```



```{r, fig.height=6, fig.width =8}
cmd.data.age <- sim.results.all %>% 
  filter(Age > 18) %>% 
  filter(Year %in% c(2004)) %>% 
  mutate(HIVneg = Population - Infected) %>% 
  group_by(Year, Gender, Age, sim.id, IP_Key.CMDStatus, scenario_name) %>% 
  summarize(Population = sum(Population),
            HIVneg = sum(HIVneg),
            Infected = sum(Infected), .groups = 'keep') %>% 
  ungroup() %>% 
  pivot_wider(id_cols = c(Year, Gender, Age, sim.id, scenario_name),
              names_from = c(IP_Key.CMDStatus),
              values_from = c(Population, HIVneg, Infected))  %>% 
  mutate(Population_total = Population_CMD_pos + Population_CMD_neg + Population_CMD_recovered + Population_CMD_treated,
         HIVneg_total = HIVneg_CMD_pos + HIVneg_CMD_neg + HIVneg_CMD_recovered + HIVneg_CMD_treated,
         Infected_total = Infected_CMD_pos + Infected_CMD_neg + Infected_CMD_recovered + Infected_CMD_treated) %>% 
  mutate(CMD_prev_overall = case_when(Population_total == 0 ~ 0,
                                    Population_total > 0 ~ Population_CMD_pos/Population_total),
         CMD_prev_HIVneg = case_when(HIVneg_total == 0 ~ 0,
                                    HIVneg_total > 0 ~ HIVneg_CMD_pos/HIVneg_total),
         CMD_prev_Infected = case_when(Infected_total == 0 ~ 0,
                                    Infected_total > 0 ~ Infected_CMD_pos/Infected_total)) %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

# Define age bins
age_bins = c(18, 25, 30, 40, 45, 50, 60, 99)
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
cmd.data.age <- cmd.data.age %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
cmd.data.age$AgeBin_index = factor(cmd.data.age$AgeBin,labels = 1:length(age_labels))

cmd.data.age.mean <- cmd.data.age %>% 
  group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>% 
  summarize(mean.Overall = mean(CMD_prev_overall), sd.Overall = sd(CMD_prev_overall),
            mean.HIVneg = mean(CMD_prev_HIVneg), sd.HIVneg = sd(CMD_prev_HIVneg),
            mean.Infected = mean(CMD_prev_Infected), sd.Infected = sd(CMD_prev_Infected),
              .groups = 'keep') %>% 
  mutate(lb.Overall = max(mean.Overall - 2* sd.Overall, 0), ub.Overall = mean.Overall + 2*sd.Overall,
         lb.HIVneg = max(mean.HIVneg - 2* sd.HIVneg, 0), ub.HIVneg = mean.HIVneg + 2*sd.HIVneg,
         lb.Infected = max(mean.Infected - 2* sd.Infected, 0), ub.Infected = mean.Infected + 2*sd.Infected
)

p <- cmd.data.age.mean %>% 
  filter(scenario_name == "baseline") %>% 
  ggplot() + 
  # data comparison
  geom_point(obs.cmdprev.sheet,
             mapping = aes(x = AgeBin_index, y = 100*CMDPrevalence), 
             color = 'orange', size = 4) + 
  geom_errorbar(obs.cmdprev.sheet,
             mapping = aes(x = AgeBin_index, ymin = 100*CMDPrevalence.lb, ymax = 100*CMDPrevalence.ub), color = 'orange', size = 2) + 
  # sim results
  geom_point(mapping = aes(x = AgeBin_index, y = 100*mean.Overall), 
             size = 4, color = 'darkgreen', shape = 15) + 
  # geom_errorbar(mapping = aes(x = AgeBin_index, ymin = 100*lb.Overall, ymax = 100*ub.Overall),
  #               width = .3, size =2, color = 'darkgreen') + 
  facet_grid(cols = vars(Gender)) + 
  xlab("Age") + ylab("") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    ) + 
  ylab("Depression Prevalence by Age") + 
  scale_y_continuous(limits =c(0,100)) +  coord_cartesian(ylim = c(0, 30)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_depression_age_prev.pdf",
       width = 10, height = 5, units = "in")

```

## Incidence

```{r}
data <- EMODAnalyzeR::calculate.prevalence(
  sim.results.all %>% filter(Age >=15),
         stratify_columns = c("Year", "Gender", "sim.id", "scenario_name"),
         numerator = "Infected",
         denominator = "Population")

data.mean <- data %>% filter(Year >= 2004) %>% 
  group_by(Year, Gender, scenario_name) %>%
  summarize(sum(Infected))

data.mean <- data %>%
    dplyr::group_by(Year, Gender, scenario_name) %>%
    dplyr::summarise(Prevalence = mean(Prevalence), .groups = 'keep')


rescale.ratio <- data.mean %>% pivot_wider(id_cols = c("Year", "Gender"), values_from = c("Prevalence"), names_from= ("scenario_name")) %>% 
  mutate(ratio = screen.tt/baseline)
```


### Deaths

```{r, fig.width=8in}
data <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>%
  filter(Year >= 1985, Year <=2040, Age >= 15) %>% 
  group_by(Year, Gender, sim.ix, sim.id, scenario_name) %>% 
  summarize(Deaths = sum(Died_from_HIV * pop.scaling.factor), .groups = 'keep') %>%  
  ungroup()

data.mean <- data %>% 
  group_by(Year, Gender, scenario_name) %>% 
  dplyr::summarise(Deaths = mean(Deaths), .groups = 'keep') 

p <- EMODAnalyzeR::emodplot.by_gender(data, 2015, 2040, 
                        "Deaths", title = "HIV deaths") 

p + #scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab("") + 
  #scale_color_manual(values = c("blue","red"))
  scale_color_manual(values = c("blue","red","darkgreen","orange"))

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_HIV_deaths.pdf",
#       width = 8, height = 6, units = "in")
```

Deaths by scenario
```{r}
#data %>% group_by(Year, Gender, scenario_name) %>% summarize(mean(Deaths)) %>% filter(Year >= 2015)
data %>% filter(Year >= 2020) %>%  group_by(Gender, Year, scenario_name, sim.ix) %>%  summarize(Deaths = sum(Deaths)) %>% 
   group_by(Gender, Year, scenario_name) %>% summarize(Deaths = mean(Deaths)) 


deaths.dat <- data %>% filter(Year >= 2020) %>%  group_by(Gender, Year, scenario_name, sim.ix) %>%  summarize(Deaths = sum(Deaths)) %>% 
   group_by(Gender, Year, scenario_name) %>% summarize(Deaths = mean(Deaths))  %>% ungroup() %>% 
  inner_join(
    rescale.ratio %>% select(Year, Gender, ratio), 
    by = c("Year", "Gender")
  ) %>% 
  mutate(Deaths.adjusted = case_when(scenario_name == "screen.tt" ~ Deaths/ratio,
                                     scenario_name != "screen.tt" ~Deaths))

deaths.dat %>% group_by(Gender, scenario_name) %>% summarize(sum(Deaths.adjusted), sum(Deaths))

deaths.dat %>% group_by( scenario_name) %>% summarize(sum(Deaths.adjusted), sum(Deaths))
```

### New cases

```{r, fig.width=8in}
 data <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>%
  filter(Year >= 1985, Year <=2040) %>% 
  group_by(Year, Gender, sim.id, sim.ix, scenario_name) %>% 
  summarize(NewCases = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>%  
  ungroup() %>% 
  group_by(Year, Gender, sim.id, sim.ix, scenario_name) %>% 
  summarize(NewCases.sd = sd(NewCases), NewCases = mean(NewCases)) %>% 
  ungroup()# %>% 
  
p <- EMODAnalyzeR::emodplot.by_gender(data, 1990, 2040, 
                        "NewCases", title = "New HIV Infections") 

p + #scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab("") + 
  scale_color_manual(values = c("blue","red","darkgreen","orange"))

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_HIV_casdes.pdf",
#       width = 8, height = 6, units = "in")

```

New cases by scenario
```{r}
data %>% filter(Year >= 2020) %>%  group_by(Gender, scenario_name, sim.ix) %>% summarize(NewCases = sum(NewCases)) %>% 
  group_by(Gender, scenario_name) %>% summarize(NewCases = mean(NewCases))


cases.dat <- data %>% filter(Year >= 2020) %>%  group_by(Gender, Year, scenario_name, sim.ix) %>%  summarize(NewCases = sum(NewCases)) %>% 
   group_by(Gender, Year, scenario_name) %>% summarize(NewCases = mean(NewCases))  %>% ungroup() %>% 
  inner_join(
    rescale.ratio %>% select(Year, Gender, ratio), 
    by = c("Year", "Gender")
  ) %>% 
  mutate(NewCases.adjusted = case_when(scenario_name == "screen.tt" ~ NewCases/ratio,
                                     scenario_name != "screen.tt" ~NewCases))

cases.dat %>% group_by(Gender, scenario_name) %>% summarize(sum(NewCases.adjusted), sum(NewCases))


cases.dat %>% group_by(scenario_name) %>% summarize(sum(NewCases.adjusted), sum(NewCases))

```


## ART numbers over time

```{r}
ingest.file.base = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/202301_Nyanza_Baseline_MalariaOngoing_original/Data/calibration_ingest_form_Nyanza.xlsm"

obs.onart.sheet <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-OnART")
```


```{r, fig.width=8}
sim.onart <- sim.results.all %>% 
  dplyr::group_by(Year, Gender, sim.id, scenario_name) %>% 
  dplyr::summarize(On_ART = sum(On_ART * pop.scaling.factor), .groups = "keep") %>% 
  ungroup()

p <- EMODAnalyzeR::emodplot.by_gender(sim.onart, 2000, 2025, 
                        "On_ART", title = "Population on ART") + 
    ylab("Number on ART")

p + 
  geom_point(data = obs.onart.sheet %>% 
               filter(Province != "All", 
                      Gender %in% c("Male", "Female"), 
                      AgeBin == "[15:100)") %>%
              group_by(Year, Gender) %>% 
              summarize(OnART = sum(OnART)) %>% ungroup(),
              mapping = aes(x = Year, y = OnART)) + 
  geom_errorbar(data = obs.onart.sheet %>% 
                  filter(Province != "All", 
                         Gender %in% c("Male", "Female"), 
                         AgeBin == "[15:100)") %>%
              group_by(Year, Gender) %>% 
              summarize(OnART = sum(OnART)) %>% ungroup() %>% 
              mutate(lb = OnART - OnART/5,
                     ub = OnART + OnART/5),
              mapping = aes(x = Year, ymin = lb, ymax = ub)) + 
  scale_color_manual(values = c("blue","red","darkgreen","orange"))

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_onART.pdf",
#        width = 8, height = 6, units = "in")
```

```{r}
sim.onart.mean <- sim.onart %>% group_by(Year, Gender, scenario_name) %>% summarize(mean(On_ART))

sim.onart.mean %>% filter(Year > 2015)
```

## 90-90-90 

### Diagnosis coverage over time

```{r}
data.diag <- sim.results.all %>% 
  filter(Age >=15) %>% 
  group_by(Year, Gender,sim.id,scenario_name) %>% 
  summarize(Diagnosed = sum(Diagnosed), Infected = sum(Infected), .groups = "keep") %>% 
  ungroup() %>% 
  mutate(Diagnosed = case_when(Infected == 0 ~ 0,
                               Infected > 0 ~ Diagnosed/Infected)) 

p <- EMODAnalyzeR::emodplot.by_gender(data.diag, 2000, 2040, 
                        "Diagnosed", title = "Diagnosed PLHIV") 

p + scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab("% PLHIV Diagnosed") + 
  scale_color_manual(values = c("blue","red", "darkgreen"))

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_diagnosed.pdf",
#        width = 8, height = 6, units = "in")
```

```{r}
data.diag.mean <- data.diag %>% group_by(Year ,Gender, scenario_name) %>% summarize(mean(Diagnosed))

data.diag.mean %>% filter(Year > 2015)
```


### ART coverage over time

```{r}
data.artcov <- sim.results.all %>% 
  filter(Age >=15) %>% 
  group_by(Year, Gender,sim.id,scenario_name) %>% 
  summarize(On_ART = sum(On_ART), Diagnosed = sum(Diagnosed), .groups = "keep") %>% 
  ungroup() %>% 
  mutate(On_ART = case_when(On_ART == 0 ~ 0,
                               On_ART > 0 ~ On_ART/Diagnosed)) 

p <- EMODAnalyzeR::emodplot.by_gender(data.artcov, 2000, 2040, 
                        "On_ART", title = "ART Coverage") 

p + scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab("% Diagnosed and On ART") + 
  scale_color_manual(values = c("blue","red", "darkgreen"))

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_art_coverage.pdf",
#        width = 8, height = 6, units = "in")
```

```{r}
data.artcov.mean <- data.artcov %>% group_by(Year ,Gender, scenario_name) %>% summarize(mean(On_ART))

data.artcov.mean %>% filter(Year > 2015)
```

## DALY calculations

```{r}
dalys.baseline <-  EMODAnalyzeR::calculate.DALY(sim.results.all %>% 
                                                 mutate(pop_scaling_factor = pop.scaling.factor) %>% 
                                                 filter(scenario_name =="baseline"),
                             infected_weight = 0.274, art_weight = 0.078, discount_start_year = 2023, discount_percent = 0.03, life_expectancy = 80)


dalys.uni.tt <-  EMODAnalyzeR::calculate.DALY(sim.results.all %>% 
                                                 mutate(pop_scaling_factor = pop.scaling.factor) %>% 
                                                 filter(scenario_name =="uni.tt"),
                             infected_weight = 0.274, art_weight = 0.078, discount_start_year = 2023, discount_percent = 0.03, life_expectancy = 80)


dalys.screen.tt <-  EMODAnalyzeR::calculate.DALY(sim.results.all %>% 
                                                 mutate(pop_scaling_factor = pop.scaling.factor) %>% 
                                                 filter(scenario_name =="screen.tt"),
                             infected_weight = 0.274, art_weight = 0.078, discount_start_year = 2023, discount_percent = 0.03, life_expectancy = 80)


dalys.baseline$scenario_name  = "baseline"
dalys.uni.tt$scenario_name = "uni.tt"
dalys.screen.tt$scenario_name = "screen.tt"

dalys <- rbind(dalys.baseline, dalys.uni.tt, dalys.screen.tt)

dalys %>% filter(year > 2020) %>% group_by(scenario_name) %>% summarize(sum(daly))
```

```{r}
p = ggplot() +
  geom_line( dalys %>% filter(year >= 2015),
    mapping = aes(x = year, y = daly, color = scenario_name), 
    size = 1.0) + 
  #scale_y_continuous(limits = c(0.05,.22)) + 
  #facet_wrap( ~ Gender, ncol=2) +
  xlab("Year")+ylab("") + 
  ggtitle("HIV-related DALYs by year") + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(1980,2040,10)) + 
  scale_color_manual(values = c("blue","red")) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/MATUMAINI/Analysis/treatment_dalys.pdf",
       width = 8, height = 6, units = "in")

```

## Person-Years Lived with Depression

Calculate the number of person-years lived with depression
* For the baseline scenario, multiply all of the depressed people by 270/365
* For the treatment scenario, multiply all of hte depressed people by 90/365

```{r}
data <- sim.results.all %>% 
  #mutate(Year = ceiling(Year)) %>% 
  filter(Year >= 1985,
         IP_Key.CMDStatus == "CMD_pos") %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(deps = sum(Population * pop.scaling.factor), 
            deps.onart = sum(On_ART * pop.scaling.factor),
            .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(deps = mean(deps), deps.onart = mean(deps.onart))


(data %>% filter(scenario_name == "baseline") %>% filter(Year <= 2020) %>% .$deps %>% sum)*270/365
(data %>% filter(scenario_name == "baseline") %>% filter(Year > 2020) %>% .$deps %>% sum)*270/365


(data %>% filter(scenario_name == "uni.tt") %>% filter(Year <= 2020) %>% .$deps %>% sum)*270/365
(data %>% filter(scenario_name == "uni.tt") %>% filter(Year > 2020) %>% .$deps %>% sum)*90/365


(data %>% filter(scenario_name == "screen.tt") %>% filter(Year <= 2020) %>% .$deps %>% sum)*270/365
# need to weight this according to people with and without HIV; so this isn't crazy
(data %>% filter(scenario_name == "screen.tt") %>% filter(Year > 2020) %>% ungroup() %>% summarize(deps = sum(deps), deps.onart = sum(deps.onart)))
(14980219 - 1076090)*270/365 + 1076090*90/365
 
```
HIV positive people living iwth depression
```{r}
data <- sim.results.all %>% 
  #mutate(Year = ceiling(Year)) %>% 
  filter(Year >= 1985,
         IP_Key.CMDStatus == "CMD_pos", ) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(deps = sum(Infected * pop.scaling.factor), 
            deps.onart = sum(On_ART * pop.scaling.factor), 
            .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(deps = mean(deps), deps.onart = mean(deps.onart))


(data %>% filter(scenario_name == "baseline") %>% filter(Year <= 2020) %>% .$deps %>% sum)
(data %>% filter(scenario_name == "baseline") %>% filter(Year > 2020) %>% .$deps %>% sum)*270/365


(data %>% filter(scenario_name == "uni.tt") %>% filter(Year <= 2020) %>% .$deps %>% sum)*270/365
(data %>% filter(scenario_name == "uni.tt") %>% filter(Year > 2020) %>% .$deps %>% sum)*90/365


(data %>% filter(scenario_name == "screen.tt") %>% filter(Year <= 2020) %>% .$deps %>% sum)*270/365
# need to weight this according to people with and without HIV; so this isn't crazy
(data %>% filter(scenario_name == "screen.tt") %>% filter(Year > 2020) %>% .$deps %>% sum)*90/365
(data %>% filter(scenario_name == "screen.tt") %>% filter(Year > 2020) %>% ungroup() %>% summarize(deps = sum(deps), deps.onart = sum(deps.onart)))
(14980219 - 1076090) + 1076090*90/365

```
